---
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: yes
--- 
             

# plus sc10x            
      
run cellranger with Spp1-EGFP added reference index                          
         
##### load dependancies                
```{r message=FALSE, warning=FALSE, include=FALSE}
source("F:/Rstudio_analysis/analysis.10x.r")
```


three models: EAE, AD, SIMPLE      
each has one GFP(Spp1+), MIG(total microglia), CTL(WT)        
AD.GFP.2 is from homozygous model while others are all heterozygous, so need to be excluded before final clustering         
     

         
loading 65k cells, CX3CR1+          
demo, cellranger called 39,425 cells                    
plus, cellranger called 43,176 cells            
       
## load 10x data      

```{r}
filt.10x <- Read10X(data.dir = "../output_plus_exogene/filtered_feature_bc_matrix/")
``` 


```{r}
GEX <- filt.10x$`Gene Expression`
FB <- filt.10x$`Antibody Capture`
```


### check datasets   
```{r message=FALSE, warning=FALSE}
dim(GEX)
GEX[1:6,1:6]
```


```{r}
dim(FB)
FB[,1:6]
```


```{r}
rowSums(FB)
```

```{r}
rowSums(FB>0)
```

## FB     
      
```{r}
# build seurat object
FB.seur <- CreateSeuratObject(counts = FB,project = "Spp1ND")

FB.seur
```


```{r}
rownames(FB.seur)
```


### normalization     
    
perform Seurat 'Demultiplexing with hashtag oligos(HTOs)     
ref https://satijalab.org/seurat/articles/hashing_vignette.html       
    
```{r}
# normalize
FB.seur <- NormalizeData(FB.seur)
FB.seur <- FindVariableFeatures(FB.seur, selection.method = "mean.var.plot")
FB.seur <- ScaleData(FB.seur, features = VariableFeatures(FB.seur))

# independent assay for HTO data  
FB.seur[['HTO']] <- CreateAssayObject(counts = FB)
FB.seur <- NormalizeData(FB.seur, assay = 'HTO', normalization.method = 'CLR')
```


### check demux         

first define FB colors based on conditions                      

```{r fig.height=6, fig.width=8.1}
scales::show_col(ggsci::pal_igv("default")(49))
```

```{r}
color.FB <- ggsci::pal_igv("default")(49)[c(8,33,40,
                                            34,26,1,28,
                                            2,43,18)]

#2,13,33,1,15,
#34,26,28,40,18

level.FB <- c(rownames(FB.seur))

color.FBraw <-  c("#FF6C91","lightgrey",color.FB)
```


```{r}
scales::show_col(color.FBraw, ncol = 5)
scales::show_col(color.FB, ncol = 5)
```



```{r fig.height=6.5, fig.width=15, message=FALSE, warning=FALSE}
par(mfrow=c(2,5))

#plot(sort(rowSums(t(FB))),
#     xlab="reordered cells", 
#     ylab="UMI counts", log="xy",
#     main="sum")


plot(sort(t(FB)[,1]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[1])
plot(sort(t(FB)[,2]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[2])
plot(sort(t(FB)[,3]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[3])
plot(sort(t(FB)[,4]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[4])
plot(sort(t(FB)[,5]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[5])
plot(sort(t(FB)[,6]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[6])
plot(sort(t(FB)[,7]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[7])
plot(sort(t(FB)[,8]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[8])
plot(sort(t(FB)[,9]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[9])
plot(sort(t(FB)[,10]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[10])
```


#### range 'q'         

##### q0.50 ~ 0.99       

```{r include=FALSE, paged.print=FALSE}
FB.test <- FB.seur
#cut.list <- list()

table.demux <- data.frame(sample=c("quantile","Doublet",rownames(FB.test),"Negative"))

for(i in 50:99){
  FB.test <- HTODemux(FB.test, assay = "HTO", positive.quantile = i/100)
  table.demux <- cbind(table.demux,
                       c(i/100,table(FB.test$hash.ID)[c("Doublet",rownames(FB.test),"Negative")]))
}
rownames(table.demux) <- table.demux$sample
table.demux <- table.demux[,2:ncol(table.demux)]
table.demux <- data.frame(t(table.demux))
rownames(table.demux) <- NULL
table.demux
```



```{r fig.width=18, fig.height=10}
#color.FB <- scales::hue_pal()(10)
par(mfrow=c(3,5))


plot(table.demux$Doublet, type="p", col="#FF6C91", pch=16, ylab="Doublet")
plot(table.demux$Negative, type="p", col="lightgrey", pch=16, ylab="Negative")
plot(rowSums(table.demux[,grep("EAE|AD|SIM",colnames(table.demux))]), type="p", col="#306000", pch=16, ylab="Singlet")

plot(table.demux$quantile, pch=16, ylab="mod-quantile")
plot.new()

plot(table.demux[,2+1], type="p", col=color.FB[1], pch=16, ylab=colnames(table.demux)[2+1])
plot(table.demux[,2+2], type="p", col=color.FB[2], pch=16, ylab=colnames(table.demux)[2+2])
plot(table.demux[,2+3], type="p", col=color.FB[3], pch=16, ylab=colnames(table.demux)[2+3])
plot(table.demux[,2+4], type="p", col=color.FB[4], pch=16, ylab=colnames(table.demux)[2+4])
plot(table.demux[,2+5], type="p", col=color.FB[5], pch=16, ylab=colnames(table.demux)[2+5])

plot(table.demux[,2+6], type="p", col=color.FB[6], pch=16, ylab=colnames(table.demux)[2+6])
plot(table.demux[,2+7], type="p", col=color.FB[7], pch=16, ylab=colnames(table.demux)[2+7])
plot(table.demux[,2+8], type="p", col=color.FB[8], pch=16, ylab=colnames(table.demux)[2+8])
plot(table.demux[,2+9], type="p", col=color.FB[9], pch=16, ylab=colnames(table.demux)[2+9])
plot(table.demux[,2+10], type="p", col=color.FB[10], pch=16, ylab=colnames(table.demux)[2+10])

```


##### q0.9900 ~ 0.9999               

```{r include=FALSE, paged.print=FALSE}
FB.test <- FB.seur
#cut.list <- list()

table.demux.s <- data.frame(sample=c("quantile","Doublet",rownames(FB.test),"Negative"))

for(i in 9900:9999){
  FB.test <- HTODemux(FB.test, assay = "HTO", positive.quantile = i/10000)
  table.demux.s <- cbind(table.demux.s,
                       c(i/10000,table(FB.test$hash.ID)[c("Doublet",rownames(FB.test),"Negative")]))
}
rownames(table.demux.s) <- table.demux.s$sample
table.demux.s <- table.demux.s[,2:ncol(table.demux.s)]
table.demux.s <- data.frame(t(table.demux.s))
rownames(table.demux.s) <- NULL
table.demux.s
```


```{r fig.width=18, fig.height=10}
#color.FB <- scales::hue_pal()(10)
par(mfrow=c(3,5))


plot(table.demux.s$Doublet, type="p", col="#FF6C91", pch=16, ylab="Doublet")
plot(table.demux.s$Negative, type="p", col="lightgrey", pch=16, ylab="Negative")
plot(rowSums(table.demux.s[,grep("EAE|AD|SIM",colnames(table.demux.s))]), type="p", col="#306000", pch=16, ylab="Singlet")

plot(table.demux.s$quantile, pch=16, ylab="mod-quantile")
plot.new()

plot(table.demux.s[,2+1], type="p", col=color.FB[1], pch=16, ylab=colnames(table.demux.s)[2+1])
plot(table.demux.s[,2+2], type="p", col=color.FB[2], pch=16, ylab=colnames(table.demux.s)[2+2])
plot(table.demux.s[,2+3], type="p", col=color.FB[3], pch=16, ylab=colnames(table.demux.s)[2+3])
plot(table.demux.s[,2+4], type="p", col=color.FB[4], pch=16, ylab=colnames(table.demux.s)[2+4])
plot(table.demux.s[,2+5], type="p", col=color.FB[5], pch=16, ylab=colnames(table.demux.s)[2+5])

plot(table.demux.s[,2+6], type="p", col=color.FB[6], pch=16, ylab=colnames(table.demux.s)[2+6])
plot(table.demux.s[,2+7], type="p", col=color.FB[7], pch=16, ylab=colnames(table.demux.s)[2+7])
plot(table.demux.s[,2+8], type="p", col=color.FB[8], pch=16, ylab=colnames(table.demux.s)[2+8])
plot(table.demux.s[,2+9], type="p", col=color.FB[9], pch=16, ylab=colnames(table.demux.s)[2+9])
plot(table.demux.s[,2+10], type="p", col=color.FB[10], pch=16, ylab=colnames(table.demux.s)[2+10])

```



### demultiplexing        

(tags1-6/8/9 set q0.998, tags7/10 q0.99)                       


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.994)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.996)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.998)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# Demultiplex cells based on HTO enrichment
FB.seur <- HTODemux(FB.seur, assay = 'HTO', positive.quantile = 0.99)

table(FB.seur$HTO_classification.global)
table(FB.seur$hash.ID)[c("Doublet","Negative",rownames(FB))]
```


```{r}
# tags q0.99
#cutoff.FB <- c(37,51,30,17,12,
#               20,13,24,21,20)

# tags1-6/8/9 set q0.996
#cutoff.FB <- c(42,59,34,20,13,
#               23,13,27,25,20)

# tags1-6/8/9 set q0.998
cutoff.FB <- c(46,64,38,22,15,
               26,13,30,27,20)

names(cutoff.FB) <- rownames(FB.seur)
cutoff.FB
```


```{r fig.height=6.5, fig.width=15, message=FALSE, warning=FALSE}
par(mfrow=c(2,5))

#plot(sort(rowSums(t(FB))),
#     xlab="reordered cells", 
#     ylab="UMI counts", log="xy",
#     main="sum")


plot(sort(t(FB)[,1]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[1])
abline(h=cutoff.FB[1],col = color.FB[1])
plot(sort(t(FB)[,2]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[2])
abline(h=cutoff.FB[2],col = color.FB[2])
plot(sort(t(FB)[,3]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[3])
abline(h=cutoff.FB[3],col = color.FB[3])
plot(sort(t(FB)[,4]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[4])
abline(h=cutoff.FB[4],col = color.FB[4])
plot(sort(t(FB)[,5]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[5])
abline(h=cutoff.FB[5],col = color.FB[5])

plot(sort(t(FB)[,6]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[6])
abline(h=cutoff.FB[6],col = color.FB[6])
plot(sort(t(FB)[,7]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[7])
abline(h=cutoff.FB[7],col = color.FB[7])
plot(sort(t(FB)[,8]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[8])
abline(h=cutoff.FB[8],col = color.FB[8])
plot(sort(t(FB)[,9]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[9])
abline(h=cutoff.FB[9],col = color.FB[9])
plot(sort(t(FB)[,10]),
     xlab="reordered cells", 
     ylab="UMI counts", log="xy",
     main=rownames(FB)[10])
abline(h=cutoff.FB[10],col = color.FB[10])
```


```{r}
custom.Demux <- function(FBobj,FBcutoff){
  # define decision matrix
  dd <- FBobj@assays[['HTO']]@counts
  dd <- apply(dd, 2, function(x){
    x > FBcutoff
  })
  x1 <- colSums(dd)
  x1[x1>1] <- "Doublet"
  x1[x1==0] <- "Negative"
  x1[x1==1] <- "Singlet"

  x2 <- x1
  
  bc.slt  <- names(x1)[x1=="Singlet"]
  
  for(bc in bc.slt){
    x2[bc] <- rownames(dd)[dd[,bc]]
  }
  
  FBdf <- data.frame(HTO_classification.global=factor(x1,
                                                      levels = c("Doublet","Negative","Singlet")),
                     hash.ID=factor(x2,
                                    levels = c("Doublet","Negative",rownames(dd))))
  return(FBdf)
}

df.FB <- custom.Demux(FB.seur,cutoff.FB)
```


```{r}
dim(df.FB)
df.FB[1:10,]
```


```{r}
table(df.FB)
```


```{r paged.print=FALSE}
FB.seur@meta.data[,c("HTO_classification.global","hash.ID")] <- df.FB
FB.seur@meta.data[1:4,]
```


```{r}
## if all using same q, then run this chunk instead of several custom ones above    
#
#FB.seur$HTO_classification.global <- factor(as.character(FB.seur$HTO_classification.global),
#                                            levels = c("Doublet","Negative","Singlet"))
#FB.seur$hash.ID <- factor(as.character(FB.seur$hash.ID),
#                          levels = c("Doublet","Negative",rownames(FB.seur)))
```


```{r singlelt, fig.height=4, fig.width=4}
sl_stat <- table(FB.seur$HTO_classification.global)
barplot(sl_stat,ylim = c(0,32500),col = c("#FF6C91","lightgrey","#7CAE00"),main = "Feature Barcode statistics")
text(x=1:3*1.2-0.5,y=sl_stat+1680,paste0(sl_stat,"\n",100*round(as.numeric(sl_stat/sum(sl_stat)),4),"%"),cex = 0.75)
``` 


#### RidgePlot    
##### with ridge plots, raw    
```{r fig.width=12,fig.height=6,message=FALSE, warning=FALSE}
FB.seur@active.ident <- factor(FB.seur$HTO_maxID,levels=rownames(FB.seur))

RidgePlot(FB.seur, assay = 'HTO', features = rownames(FB.seur[['HTO']]),same.y.lims= TRUE, ncol=5,
          cols = color.FB) 
```


##### with ridge plots, filtered    

```{r fig.width=12,fig.height=7,message=FALSE, warning=FALSE}
RidgePlot(FB.seur, assay = 'HTO', features = rownames(FB.seur[['HTO']]), ncol=5,same.y.lims= TRUE,
          cols = c("#FF6C91","lightgrey",color.FB),group.by = "hash.ID") 
```


#### tSNE for HTOs     
     
     
```{r message=FALSE, warning=FALSE}
# first, remove negative cells from th object
#FB.seur.subset <- FB.seur

# Calculate a tSNE embedding of the HTO data
#DefaultAssay(FB.seur.subset) <- "HTO"

#FB.seur.subset <- ScaleData(FB.seur.subset, features = rownames(FB.seur.subset), verbose = FALSE)
#FB.seur.subset <- RunPCA(FB.seur.subset, features = rownames(FB.seur.subset), approx = FALSE)
#FB.seur.subset <- RunTSNE(FB.seur.subset, dims = 1:10, perplexity = 500, check_duplicates = FALSE)


#saveRDS(FB.seur.subset, "FB0829.seur.subset.rds")
FB.seur.subset <- readRDS("FB0829.seur.subset.rds")
```


```{r include=FALSE, paged.print=FALSE}
FB.seur.subset@meta.data[,c("HTO_classification.global","hash.ID")] <- df.FB
FB.seur.subset@meta.data[1:4,]
```


```{r fig.width=5.5,fig.height=8.6}
multiplot(
DimPlot(FB.seur.subset, order =  rev(rownames(FB.seur)),
        cols = color.FB) + labs(title = "FB Max_ID"), 
DimPlot(FB.seur.subset, order = rev(c("Negative",rownames(FB.seur),"Doublet")), 
        group.by = 'hash.ID', label = F,
        cols = c("lightgrey",color.FB,"#FF6C91")) + 
  labs(title = "FB Filtered_ID") + theme(plot.title = element_text(hjust = 0)) ,
cols = 1)
```


### stat    

```{r}
FB.seur$HTO_classification.global <- factor(as.character(FB.seur$HTO_classification.global),
                                            levels = c("Doublet","Negative","Singlet"))
Idents(FB.seur) <- "HTO_classification.global"
VlnPlot(FB.seur, features = "nCount_RNA", pt.size = 0, log = TRUE, cols = c("#F8766D","lightgrey","#00BA38"))
VlnPlot(FB.seur, features = "nCount_RNA", pt.size = 0, log = TRUE, cols = c("#F8766D","lightgrey","#00BA38")) + geom_jitter(alpha=0.015)
```



```{r}
table(FB.seur@meta.data$hash.ID)
```



```{r fig.width=7.2,fig.height=4}
par(mar=c(6,4,2,3))
sl_stat <- table(FB.seur$hash.ID)
barplot(sl_stat,ylim = c(0,23800),
        col = c("#FF6C91","lightgrey",color.FB),
        main = "Feature Barcode statistics",cex.names = 0.75, xaxt = "n")
axis(1,1:12*1.2-0.48 ,levels(FB.seur@meta.data$hash.ID), las=3, cex.axis=0.85)
text(x=1:12*1.2-0.45,y=sl_stat+1575,paste0(sl_stat,"\n",100*round(as.numeric(sl_stat/sum(sl_stat)),4),"%"),cex = 0.75)
```


## GEX    
    
mainly follow https://satijalab.org/seurat/articles/pbmc3k_tutorial.html    


```{r message=FALSE, warning=FALSE}
GEX.seur <- CreateSeuratObject(counts = GEX,
                               min.cells = 3,
                               min.features = 200,
                               project = "Spp1ND")
GEX.seur
```



### filtering    

#### MT genes   
```{r}
grep("^mt-",rownames(GEX),value = T)
```

```{r}
MT_gene <- grep("^mt-",rownames(GEX.seur),value = T)
GEX.seur[["percent.mt"]] <- PercentageFeatureSet(GEX.seur, features = MT_gene)

RB_gene <- grep("^Rps|^Rpl",rownames(GEX.seur),value = T)
GEX.seur[["percent.rb"]] <- PercentageFeatureSet(GEX.seur, features = RB_gene)

# Visualize QC metrics as a violin plot
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0.01)
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0)
```


```{r fig.width=15,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt") 
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA") 
plotc <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.rb")
plota + plotb + plotc
```


#### add FB info      

```{r}
GEX.seur$FB.info <- FB.seur@meta.data[rownames(GEX.seur@meta.data),"hash.ID"]
#head(GEX.seur@meta.data)
```


```{r}
table(GEX.seur$FB.info)
```


```{r fig.width=8.1, fig.height=8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = c("#FF6C91","lightgrey",color.FB),
        pt.size = 0.1, split.by = "FB.info")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = c("#FF6C91","lightgrey",color.FB),
        pt.size = 0, split.by = "FB.info")
```


```{r}
GEX.seur <- subset(GEX.seur, subset = FB.info!="Doublet" & FB.info!="Negative")
GEX.seur
```


```{r fig.width=8, fig.height=5}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0.1)
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0)
```

```{r fig.width=8.1, fig.height=8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = c("#FF6C91","lightgrey",color.FB),
        pt.size = 0.1, split.by = "FB.info")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = c("#FF6C91","lightgrey",color.FB),
        pt.size = 0, split.by = "FB.info")
```


```{r fig.width=15,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt") 
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA") 
plotc <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.rb") 
plota + plotb + plotc
```


#### filtering   


```{r}
GEX.seur <- subset(GEX.seur, subset = percent.mt < 10 & nFeature_RNA > 650 & nFeature_RNA < 3000 & nCount_RNA < 10000)
GEX.seur
```

filtered obj        
```{r fig.width=8, fig.height=5}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0.1)
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt","percent.rb"), ncol = 4, pt.size = 0)
```


```{r fig.width=8.1, fig.height=8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FBraw,
        pt.size = 0.1, split.by = "FB.info")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FBraw,
        pt.size = 0, split.by = "FB.info")
```


```{r fig.width=15,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt") 
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA") 
plotc <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.rb") 
plota + plotb + plotc
```


```{r fig.width=7.2,fig.height=4}
par(mar=c(6,4,2,3))
sl_stat <- table(FB.seur$hash.ID)
barplot(sl_stat,ylim = c(0,18800),
        col = c("#FF6C91","lightgrey",color.FB),
        main = "Feature Barcode statistics",cex.names = 0.75, xaxt = "n")
axis(1,1:12*1.2-0.48 ,levels(FB.seur@meta.data$hash.ID), las=3, cex.axis=0.85)
text(x=1:12*1.2-0.45,y=sl_stat+1375,paste0(sl_stat,"\n",100*round(as.numeric(sl_stat/sum(sl_stat)),4),"%"),cex = 0.75)
```

```{r fig.width=7.2,fig.height=4}
par(mar=c(6,4,2,3))
sl_stat <- table(GEX.seur$FB.info)
barplot(sl_stat,ylim = c(0,4200),
        col = c("#FF6C91","lightgrey",color.FB),
        main = "Feature Barcode statistics",cex.names = 0.75, xaxt = "n")
axis(1,1:12*1.2-0.48 ,levels(FB.seur@meta.data$hash.ID), las=3, cex.axis=0.85)
text(x=1:12*1.2-0.45,y=sl_stat+275,paste0(sl_stat,"\n",100*round(as.numeric(sl_stat/sum(sl_stat)),4),"%"),cex = 0.75)
```


#### check cellcycle       
```{r}
s.genes <- Hmisc::capitalize(tolower(cc.genes.updated.2019$s.genes))
g2m.genes <- Hmisc::capitalize(tolower(cc.genes.updated.2019$g2m.genes))

GEX.seur <- CellCycleScoring(GEX.seur,
                             s.features = s.genes,
                             g2m.features = g2m.genes)
```


```{r}
VlnPlot(GEX.seur, features = c("S.Score", "G2M.Score"), group.by = "FB.info", 
    ncol = 2, pt.size = 0.1)
```


```{r message=FALSE, warning=FALSE}
GEX.seur.cc <- GEX.seur

GEX.seur.cc <- NormalizeData(GEX.seur.cc)
GEX.seur.cc <- FindVariableFeatures(GEX.seur.cc)
GEX.seur.cc <- ScaleData(GEX.seur.cc)
Idents(GEX.seur.cc) <- "Phase"
RidgePlot(GEX.seur.cc, features = c("Pcna", "Top2a", "Mcm6", "Mki67"), ncol = 2)
```

```{r message=FALSE, warning=FALSE}
GEX.seur.cc <- RunPCA(GEX.seur.cc, features = c(s.genes, g2m.genes))
DimPlot(GEX.seur.cc, reduction = 'pca')
```



### Markers and Clusters            

#### Normalizing          

```{r}
GEX.seur <- NormalizeData(GEX.seur, normalization.method = "LogNormalize", scale.factor = 10000)
```


```{r message=FALSE, warning=FALSE,fig.width=12,fig.height=5}
GEX.seur <- FindVariableFeatures(GEX.seur, selection.method = "vst", nfeatures = 1500)

# Identify the 10 most highly variable genes
#top10 <- head(VariableFeatures(GEX.seur), 10)
top20 <- head(VariableFeatures(GEX.seur), 20)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(GEX.seur)
plot2 <- LabelPoints(plot = plot1, points = top20, repel = T)
plot1 + plot2
```


```{r}
head(VariableFeatures(GEX.seur), 200)
```


```{r}
GEX.seur <- ScaleData(GEX.seur, features = rownames(GEX.seur))
```

#### PCA       

```{r}
# exclude MT genes  and more 

#DIG <- grep("^Tra|^Trb|^Trg|^Trd|^Tcr|^Igm|^Igh|^Igk|^Igl|Jchain|^Hsp|^Rps|^Rpl|Hbb-|Hba-|^Dnaj|^AY|^Gm|^Hist",rownames(GEX.seur),value = T)

DIG <- grep("^Tra|^Trb|^Trg|^Trd|^Tcr|^Igm|^Igh|^Igk|^Igl|Jchain|Mzb1|Vpreb|Lars2|Jun|Fos|^Hsp|^Rps|^Rpl|Hbb-|Hba-|^Dnaj|^AY|^AC|^AA|^AW|^BC|^Gm|^Hist|Rik$|-ps",
            rownames(GEX.seur),value = T)
CC_gene <- Hmisc::capitalize(tolower(as.vector(unlist(cc.genes.updated.2019))))


VariableFeatures(GEX.seur) <- setdiff(VariableFeatures(object = GEX.seur),
                                                c(MT_gene,
                                                  DIG, 
                                                  CC_gene) )

GEX.seur <- RunPCA(GEX.seur, features = VariableFeatures(GEX.seur))
```


```{r}
length(VariableFeatures(GEX.seur))
head(VariableFeatures(GEX.seur),300)
```


```{r fig.width=11.8,fig.height=4.5}
DimPlot(GEX.seur, reduction = "pca",dims = 1:2, group.by = "orig.ident") +
  DimPlot(GEX.seur, reduction = "pca",dims = 3:4, group.by = "orig.ident")
```

```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "pca",dims = 1:2, group.by = "FB.info", cols = color.FB) +
  DimPlot(GEX.seur, reduction = "pca",dims = 3:4, group.by = "FB.info", cols = color.FB)
```


```{r pcsheat,fig.width=12,fig.height=15}
DimHeatmap(GEX.seur, dims = 1:12, cells = 1500, balanced = TRUE,ncol = 4)
```


##### decide PCs to use          
     
```{r}
ElbowPlot(GEX.seur,ndims = 50)
```


```{r}
PCs <- 1:25
GEX.seur <- FindNeighbors(GEX.seur, dims = PCs, k.param = 10)
GEX.seur <- FindClusters(GEX.seur, method = 'igraph' ,resolution = 1.5)
```


#### Run UMAP/tSNE    

```{r}
GEX.seur <- RunTSNE(GEX.seur, dims=PCs, complexity = 100)
GEX.seur <- RunUMAP(GEX.seur, dims=PCs, n.neighbors = 50, seed.use = 666)
```


```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "tsne", label = T, group.by = "seurat_clusters") + 
  DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters")
```


```{r fig.width=7.5,fig.height=6}
FeaturePlot(GEX.seur, reduction = "umap", features = c("nFeature_RNA","nCount_RNA","percent.mt","percent.rb"))
```


```{r  fig.width=15.5, fig.height=6.4}
DimPlot(GEX.seur, label = F, pt.size = 0.05, repel = F, reduction = 'tsne', group.by = "FB.info", split.by = "FB.info", 
        ncol = 5, cols = color.FB)
DimPlot(GEX.seur, label = F, pt.size = 0.05, repel = F, reduction = 'umap', group.by = "FB.info", split.by = "FB.info", 
        ncol = 5, cols = color.FB)
``` 


```{r eval=FALSE, include=FALSE, paged.print=TRUE}
#GEX.seur$cnt <- factor(gsub(".1$|.2$","",as.character(GEX.seur$FB.info)),
#                       levels = c("P05.CTR","P05.MIG","P05.GFP",
#                                  "P28.CTR","P28.MIG","P28.GFP"))
#color.cnt <- color.FB[c(10,9,7,
#                        5,4,1)]
```


```{r fig.width=11,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "FB.info", cols = color.FB)
```



#### check some markers  

```{r}
markers.mig <- c("Ptprc",#"Cd3d","Cd3e","Cd19",
                 "Cd74","Lyz2","Ccl4",
                 "Aif1","P2ry12","C1qa","Spp1",
                 "Top2a","Pcna","Mki67","Mcm6",
                 "Cx3cr1","Il4ra","Il13ra1","Spp1-EGFP",
                 "Fabp5","Hmox1","Ms4a7","Cenpa")
```


```{r fig.width=12, fig.height=12.5}
FeaturePlot(GEX.seur, 
            features = markers.mig,
            ncol = 4)
```

```{r fig.width=7.5, fig.height=5}
DotPlot(GEX.seur, features = markers.mig, group.by = "FB.info",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1))+ scale_y_discrete(limits=rev)
```

```{r fig.width=7.5, fig.height=5}
DotPlot(GEX.seur, features = markers.mig, group.by = "seurat_clusters",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1))+ scale_y_discrete(limits=rev)
```


```{r fig.width=7.5, fig.height=6}
cowplot::plot_grid(
pheatmap::pheatmap(table(FB.info=GEX.seur$FB.info,
      clusters=GEX.seur$seurat_clusters)[c(3:12),],
                   main = "Cell Count",
                   gaps_row = c(3,7),
      #gaps_col = c(12,13,14),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.0f", legend = F, silent = T)$gtable,

pheatmap::pheatmap(100*rowRatio(table(FB.info=GEX.seur$FB.info,
                                clusters=GEX.seur$seurat_clusters)[c(3:12),]),
                   main = "Cell Ratio",
                   gaps_row = c(3,7),
      #gaps_col = c(12,13,14),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.1f", legend = F, silent =T)$gtable,
ncol = 1)
```


### markers          


#### sort_clusters          


```{r}
GEX.seur$sort_clusters <- factor(GEX.seur$seurat_clusters,
                                 levels = c(1,3,0,2,10,9,
                                            19,21,
                                            4,16,13,11,20,
                                            5,12,14,17,
                                            18,6,8,7,15,22,23))
```


```{r fig.width=7.5, fig.height=6}
cowplot::plot_grid(
pheatmap::pheatmap(table(FB.info=GEX.seur$FB.info,
      clusters=GEX.seur$sort_clusters)[c(3:12),],
                   main = "Cell Count",
                   gaps_row = c(3,7),
      #gaps_col = c(12,13,14),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.0f", legend = F, silent = T)$gtable,

pheatmap::pheatmap(100*rowRatio(table(FB.info=GEX.seur$FB.info,
                                clusters=GEX.seur$sort_clusters)[c(3:12),]),
                   main = "Cell Ratio",
                   gaps_row = c(3,7),
      #gaps_col = c(12,13,14),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.1f", legend = F, silent =T)$gtable,
ncol = 1)
```


```{r fig.width=7.5, fig.height=5}
DotPlot(GEX.seur, features = markers.mig, group.by = "sort_clusters",
        cols = c("midnightblue","darkorange1")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1))+ scale_y_discrete(limits=rev)
```


#### check some markers                 



```{r fig.width=9,fig.height=5.4}
check.Cell2017 <- c("Hexb","Cst3","P2ry12","Cx3cr1",
                    "Cd9","Ctsd","Cst7","Lpl",
                    "Mrc1","Cd163","S100a4","Cd74",
                    "Cd79b","Rag1","Trbc2","Nkg7",
                    "S100a9","Camp"
                    )

DotPlot(GEX.seur, features = check.Cell2017, group.by = "sort_clusters",
                         cols = c("midnightblue","darkorange1")) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1))#+ scale_y_discrete(limits=rev)
```


```{r fig.width=9,fig.height=5.4}
markers.Sci2019 <- c("Tmem119","Hexb","Slc2a5","P2ry12","Siglech","Trem2","Sparc","Olfml3",  # Microglia
                     "Mrc1","Lyve1","Cd163","Siglec1","Pf4","Ms4a7","Cbr2",  # CAMs
                     "Ly6c2","Ccr2","Plac8","Anxa8","Nr4a1","Mertk","Zbtb26","Cd209a",  # Monocyte-derived
                     "Flt3","Zbtb46","Batf3","Itgae","Clec9a",  # DCs
                     "Tubb3"  # local added
                     )

DotPlot(GEX.seur, features = markers.Sci2019, group.by = "sort_clusters",
                         cols = c("midnightblue","darkorange1")) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1))#+ scale_y_discrete(limits=rev)
```


```{r}
c("Xist","Tsix","Uty","Ddx3y","Eif2s3y","Kdm5d") %in% VariableFeatures(GEX.seur)
```

```{r fig.width=5.4,fig.height=5.4}
xy.genes <- c("Xist","Tsix","Uty","Ddx3y","Eif2s3y","Kdm5d")

DotPlot(GEX.seur, features = xy.genes, group.by = "sort_clusters",
                         cols = c("midnightblue","darkorange1")) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1))#+ scale_y_discrete(limits=rev)
```

```{r fig.width=5.4,fig.height=3.4}
xy.genes <- c("Xist","Tsix","Uty","Ddx3y","Eif2s3y","Kdm5d")

DotPlot(GEX.seur, features = xy.genes, group.by = "FB.info",
                         cols = c("midnightblue","darkorange1")) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1))#+ scale_y_discrete(limits=rev)
```


#### all markers                


```{r message=FALSE, warning=FALSE, paged.print=TRUE}
# find markers for every cluster compared to all remaining cells, report only the positive ones
Idents(GEX.seur) <- "sort_clusters"

#GEX.markers.pre <- FindAllMarkers(GEX.seur, only.pos = TRUE, min.pct = 0.05,
#                                  test.use = "MAST",
#                                  #test.use = "wilcox",
#                                  logfc.threshold = 0.25)
GEX.markers.pre <- read.table("sc10x_LYN.marker.sort0829.csv", header = TRUE, sep = ",")
GEX.markers.pre %>% group_by(cluster) %>% top_n(n = 8, wt = avg_log2FC)
```



```{r eval=FALSE, include=FALSE}
write.table(GEX.markers.pre, 
            "sc10x_LYN.marker.sort0829.csv", 
            col.names = TRUE,
            row.names = FALSE,
            quote = F,
            sep = ",")
```


```{r}
GEX.markers.pre$cluster <- factor(as.character(GEX.markers.pre$cluster),
                          levels = levels(GEX.seur$sort_clusters))



markers.pre_t32 <- (GEX.markers.pre %>% group_by(cluster) %>% 
                  filter(pct.1>0.1) %>%
                   top_n(n = 32, wt = avg_log2FC) %>%
                   ungroup() %>%
  arrange(desc(avg_log2FC*pct.1),gene) %>%
                             distinct(gene, .keep_all = TRUE) %>%
                             arrange(cluster,p_val_adj))$gene


markers.pre_t48 <- (GEX.markers.pre %>% group_by(cluster) %>% 
                  filter(pct.1>0.05 & gene %in% grep("Rps|Rpl|mt-",GEX.markers.pre$gene,invert = T,value = T)) %>%
                   top_n(n = 48, wt = avg_log2FC) %>%
                   ungroup() %>%
  arrange(desc(avg_log2FC*pct.1),gene) %>%
                             distinct(gene, .keep_all = TRUE) %>%
                             arrange(cluster,p_val_adj))$gene

markers.pre_t60 <- (GEX.markers.pre %>% group_by(cluster) %>% 
                  filter(pct.1>0.01 & gene %in% grep("Rps|Rpl|mt-",GEX.markers.pre$gene,invert = T,value = T)) %>%
                   top_n(n = 60, wt = avg_log2FC) %>%
                    filter(p_val_adj < 0.01) %>%
                   ungroup() %>%
  arrange(desc(avg_log2FC*pct.1),gene) %>%
                             distinct(gene, .keep_all = TRUE) %>%
                             arrange(cluster,p_val_adj))$gene
```


```{r fig.width=7.6, fig.height=9.6}
DotPlot(GEX.seur, features = rev(markers.pre_t60[1:64]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, features = rev(markers.pre_t60[65:128]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, features = rev(markers.pre_t60[129:192]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, features = rev(markers.pre_t60[193:256]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, features = rev(markers.pre_t60[257:320]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, features = rev(markers.pre_t60[321:384]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, features = rev(markers.pre_t60[385:448]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, features = rev(markers.pre_t60[449:512]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, features = rev(markers.pre_t60[513:576]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, features = rev(markers.pre_t60[577:640]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, features = rev(markers.pre_t60[641:689]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
```



## DoubletFinder              


```{r}
library(DoubletFinder)
```

```{r include=FALSE}
# to find a better pk
sweep.res.list <- paramSweep_v3(GEX.seur, PCs = PCs, sct = FALSE) 
```

```{r echo=FALSE}
for(i in 1:length(sweep.res.list)){
  if(length(sweep.res.list[[i]]$pANN[is.nan(sweep.res.list[[i]]$pANN)]) !=0){
    if(i!=1){
      sweep.res.list[[i]] <- sweep.res.list[[i-1]]
    }else(
      sweep.res.list[[i]] <- sweep.res.list[[i+1]]
    )
  }
}
sweep.stats <- summarizeSweep(sweep.res.list, GT=FALSE)
bcmvn <- find.pK(sweep.stats)
```

```{r echo=FALSE}
pk_v <- as.numeric(as.character(bcmvn$pK))
pk_good <- pk_v[bcmvn$BCmetric==max(bcmvn$BCmetric)]
```

```{r echo=FALSE}
# specify expected doublet number     
nExp_poi <- round(0.05*length(colnames(GEX.seur)))

GEX.seur <- doubletFinder_v3(GEX.seur, PCs = PCs, pN = 0.25, pK = pk_good, 
                             nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
colnames(GEX.seur@meta.data)[ncol(GEX.seur@meta.data)] <- "DoubletFinder0.05"
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# specify expected doublet number     
nExp_poi <- round(0.1*length(colnames(GEX.seur)))

GEX.seur <- doubletFinder_v3(GEX.seur, PCs = PCs, pN = 0.25, pK = pk_good, 
                             nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
colnames(GEX.seur@meta.data)[ncol(GEX.seur@meta.data)] <- "DoubletFinder0.1"
```



```{r echo=FALSE, fig.height=4.5, fig.width=10.8}
DimPlot(GEX.seur, reduction = "umap", group.by = "DoubletFinder0.05") +
DimPlot(GEX.seur, reduction = "umap", group.by = "DoubletFinder0.1")
```


```{r fig.width=10, fig.height=6.8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        ncol = 2,
        pt.size = 0.05, group.by = "sort_clusters")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        ncol = 2,
        pt.size = 0, group.by = "sort_clusters")
```


```{r fig.height=6.8, fig.width=10, message=FALSE, warning=FALSE}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        ncol = 2,
        pt.size = 0.05, group.by = "sort_clusters", split.by = "DoubletFinder0.05")
```


```{r fig.height=6.8, fig.width=10, message=FALSE, warning=FALSE}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        ncol = 2,
        pt.size = 0.05, group.by = "sort_clusters", split.by = "DoubletFinder0.1")
```


```{r}
table(GEX.seur@meta.data[,c("sort_clusters","DoubletFinder0.05")])
```


```{r}
table(GEX.seur@meta.data[,c("sort_clusters","DoubletFinder0.1")])
```


## preAnno        



```{r}
# preAnno
GEX.seur$preAnno <- as.character(GEX.seur$seurat_clusters)

GEX.seur$preAnno[GEX.seur$preAnno %in% setdiff(levels(GEX.seur$seurat_clusters), c(21,23,22,15))] <- "Microglia"

GEX.seur$preAnno[GEX.seur$preAnno %in% c(21)] <- "MIG.lowUMI"

GEX.seur$preAnno[GEX.seur$preAnno %in% c(23)] <- "DC"
GEX.seur$preAnno[GEX.seur$preAnno %in% c(22)] <- "BAM"
GEX.seur$preAnno[GEX.seur$preAnno %in% c(15)] <- "Mono"

GEX.seur$preAnno <- factor(GEX.seur$preAnno,
                           levels = c("Microglia",
                                      "MIG.lowUMI","DC","BAM","Mono"))

# cnt
# EAE - SIM - AD
# CTL - MIG - GFP
GEX.seur$cnt <- factor(gsub(".1|.2","",as.character(GEX.seur$FB.info)),
                       levels = c("EAE.CTL","EAE.MIG","EAE.GFP",
                                  "SIM.CTL","SIM.MIG","SIM.GFP",
                                  "AD.CTL","AD.MIG","AD.GFP"))

color.cnt <- color.FB[c(3,2,1,
                        10,9,8,
                        7,6,4)]
```




```{r fig.width=10.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "preAnno") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "cnt", cols = color.cnt)
```


```{r fig.width=6.5, fig.height=3}
cowplot::plot_grid(
pheatmap::pheatmap(table(FB.info=GEX.seur$cnt,
      clusters=GEX.seur$preAnno),
                   main = "Cell Count",
                   gaps_row = c(3,6),
      #gaps_col = c(12,13,14),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.0f", legend = F, silent = T)$gtable,

pheatmap::pheatmap(100*rowRatio(table(FB.info=GEX.seur$cnt,
                                clusters=GEX.seur$preAnno)),
                   main = "Cell Ratio",
                   gaps_row = c(3,6),
      #gaps_col = c(12,13,14),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.1f", legend = F, silent =T)$gtable,
ncol = 2)
```



```{r}
#saveRDS(GEX.seur, "sc10x_LYN.marker.sort0829.rds")
```




















