---
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: yes
--- 


# plus sc10x        
      

i.P06 and P30.PBS           
check DAM signature        
            
ii. P30.PBS and P30.LPS           
check TDT difference/shift              
      
              

##### load dependancies                
```{r message=FALSE, warning=FALSE, include=FALSE}
source("I:/Shared_win/projects/RNA_normal/analysis.10x.r")
```



## cleaning up                      


### processed obj             


```{r}
GEX.seur <- readRDS("../Spp1tdt.GEX.seur.sort1006.rds")
GEX.seur
```

```{r}
color.FB <- ggsci::pal_igv("default")(49)[c(8,32,40,
                                            34,26,33,28,
                                            2,43,18)]
color.FBraw <-  c("#FF6C91","lightgrey",color.FB)
```


```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "FB.info", cols = color.FB)
```

```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "preAnno")
```

```{r fig.width=8.1, fig.height=8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FB,
        pt.size = 0.1, group.by = "FB.info")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FB,
        pt.size = 0, group.by = "FB.info")
```


```{r fig.width=15,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt", group.by = "age") 
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA", group.by = "age") 
plotc <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.rb", group.by = "age")
plota + plotb + plotc
```


### filtering            


```{r}
GEX.seur <- subset(GEX.seur, subset= preAnno %in% c("Microglia") & DoubletFinder0.05 == "Singlet")
GEX.seur
```

```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "FB.info", cols = color.FB)
```

```{r fig.width=11,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "preAnno")
```

```{r fig.width=8.1, fig.height=8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FB,
        pt.size = 0.1, group.by = "FB.info")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FB,
        pt.size = 0, group.by = "FB.info")
```


```{r fig.width=15,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt", group.by = "age") 
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA", group.by = "age") 
plotc <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.rb", group.by = "age")
plota + plotb + plotc
```


### subset1                   


```{r}
GEX.seur <- subset(GEX.seur, subset= age %in% c("P06","P30.PBS"))
GEX.seur
```

```{r}
color.FB1 <- color.FB[c(1:3,8:10)]
```


```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "FB.info", cols = color.FB1)
```

```{r fig.width=11,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "preAnno")
```

```{r fig.width=8.1, fig.height=8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FB1,
        pt.size = 0.1, group.by = "FB.info")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FB1,
        pt.size = 0, group.by = "FB.info")
```


```{r fig.width=15,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt", group.by = "age") 
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA", group.by = "age") 
plotc <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.rb", group.by = "age")
plota + plotb + plotc
```


```{r fig.width=10, fig.height=6.8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        ncol = 2,
        pt.size = 0.05, group.by = "sort_clusters")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        ncol = 2,
        pt.size = 0, group.by = "sort_clusters")
```

#### advanced              

```{r}
GEX.seur <- subset(GEX.seur, subset= percent.mt < 7.5 & nFeature_RNA > 1000 & nFeature_RNA < 3600 & nCount_RNA < 12000)
GEX.seur
```


```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "FB.info", cols = color.FB1)
```

```{r fig.width=11,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "preAnno")
```

```{r fig.width=8.1, fig.height=8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FB1,
        pt.size = 0.1, group.by = "FB.info")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        #ncol = 3, 
        ncol = 2,
        cols = color.FB1,
        pt.size = 0, group.by = "FB.info")
```


```{r fig.width=15,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt", group.by = "age") 
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA", group.by = "age") 
plotc <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.rb", group.by = "age")
plota + plotb + plotc
```


```{r fig.width=10, fig.height=6.8}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        ncol = 2,
        pt.size = 0.05, group.by = "sort_clusters")
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), 
        ncol = 2,
        pt.size = 0, group.by = "sort_clusters")
```


```{r fig.width=7.2,fig.height=4}
par(mar=c(6,4,2,3))
sl_stat <- table(GEX.seur$FB.info)
barplot(sl_stat,ylim = c(0,3800),
        col = c("#FF6C91","lightgrey",color.FB),
        main = "Feature Barcode statistics",cex.names = 0.75, xaxt = "n")
axis(1,1:12*1.2-0.48 ,levels(GEX.seur$FB.info), las=3, cex.axis=0.85)
text(x=1:12*1.2-0.45,y=sl_stat+245,paste0(sl_stat,"\n",100*round(as.numeric(sl_stat/sum(sl_stat)),4),"%"),cex = 0.75)
```


## subset1         


### re-clustering                


```{r message=FALSE, warning=FALSE,fig.width=12,fig.height=5}
GEX.seur <- FindVariableFeatures(GEX.seur, selection.method = "vst", nfeatures = 1500)

# Identify the 10 most highly variable genes
#top10 <- head(VariableFeatures(GEX.seur), 10)
top20 <- head(VariableFeatures(GEX.seur), 20)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(GEX.seur)
plot2 <- LabelPoints(plot = plot1, points = top20, repel = T)
plot1 + plot2
```


```{r}
head(VariableFeatures(GEX.seur), 300)
```


#### PCA       

```{r}
# exclude MT genes  and more 
#   add sex-related Xist/Tsix

DIG <- grep("^Tra|^Trb|^Trg|^Trd|^Tcr|^Igm|^Igh|^Igk|^Igl|Jchain|Mzb1|Vpreb|Lars2|Jun|Fos|Egr1|^Hsp|^Rps|^Rpl|Hbb-|Hba-|^Dnaj|^AC|^AI|^AA|^AW|^AY|^BC|^Gm|^Hist|Rik$|-ps|Xist|Tsix|^Ifi|^Isg|^Mcm",
            rownames(GEX.seur),value = T)
CC_gene <- Hmisc::capitalize(tolower(as.vector(unlist(cc.genes.updated.2019))))
MT_gene <- grep("^mt-",rownames(GEX.seur),value = T)

VariableFeatures(GEX.seur) <- setdiff(VariableFeatures(object = GEX.seur),
                                                c(MT_gene,
                                                  DIG, 
                                                  CC_gene) )

GEX.seur <- RunPCA(GEX.seur, features = VariableFeatures(GEX.seur))
```

```{r}
length(VariableFeatures(GEX.seur))
head(VariableFeatures(GEX.seur),500)
```



```{r fig.width=11.8,fig.height=4.5}
DimPlot(GEX.seur, reduction = "pca",dims = 1:2, group.by = "orig.ident") +
  DimPlot(GEX.seur, reduction = "pca",dims = 3:4, group.by = "orig.ident")
```

```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "pca",dims = 1:2, group.by = "FB.info", cols = color.FB1) +
  DimPlot(GEX.seur, reduction = "pca",dims = 3:4, group.by = "FB.info", cols = color.FB1)
```

```{r pcsheat,fig.width=12,fig.height=15}
DimHeatmap(GEX.seur, dims = 1:12, cells = 1500, balanced = TRUE,ncol = 4)
```


```{r paged.print=FALSE}
(GEX.seur@reductions$pca@feature.loadings %>% as.data.frame)[,1:8] %>% arrange(desc(PC_1) ) %>% head(40)
```

```{r paged.print=FALSE}
(GEX.seur@reductions$pca@feature.loadings %>% as.data.frame)[,1:8] %>% arrange(PC_1 ) %>% head(40)
```


##### decide PCs to use          
     
```{r}
ElbowPlot(GEX.seur,ndims = 50)
```

```{r}
PCs <- 1:12
GEX.seur <- FindNeighbors(GEX.seur, dims = PCs, k.param = 20)
GEX.seur <- FindClusters(GEX.seur, method = 'igraph' ,resolution = 1)
```


#### Run UMAP/tSNE    

```{r}
GEX.seur <- RunTSNE(GEX.seur, dims=PCs, complexity = 100)
GEX.seur <- RunUMAP(GEX.seur, dims=PCs, n.neighbors = 50, seed.use = 253)
```


```{r include=FALSE}
#saveRDS(GEX.seur,"Spp1tdt.subset1_P06_P30PBS.sort1007.rds")
GEX.seur <- readRDS("./Spp1tdt.subset1_P06_P30PBS.new1008.rds")
```


```{r fig.width=10.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "tsne", label = T) + DimPlot(GEX.seur, reduction = "umap", label = T)
```


```{r fig.width=7.5,fig.height=6}
FeaturePlot(GEX.seur, reduction = "umap", features = c("nFeature_RNA","nCount_RNA","percent.mt","percent.rb"))
```


```{r  fig.width=10, fig.height=6.4}
DimPlot(GEX.seur, label = F, pt.size = 0.05, repel = F, reduction = 'umap', group.by = "FB.info", split.by = "FB.info", 
        ncol = 3, cols = color.FB1)
``` 


```{r fig.width=11.5,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters") +
  DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "FB.info", cols = color.FB1)
```


#### check some markers  

```{r}
markers.mig <- c("Ptprc",#"Cd3d","Cd3e","Cd19",
                 "Cd74","Lyz2","Ccl4",
                 "Aif1","P2ry12","C1qa","Spp1",
                 "Top2a","Pcna","Mki67","Mcm6",
                 "Cx3cr1","Il4ra","Il13ra1","Fabp5",
                 "Hmox1","Ms4a7","Pf4","Tubb3",
                 "tdTomato-head","tdTomato-mid","tdTomato-tail","CreERT2"
                 )
```



```{r fig.width=12, fig.height=15}
FeaturePlot(GEX.seur, 
            features = markers.mig,
            ncol = 4)
```



```{r fig.width=9,fig.height=5.4}
DotPlot(GEX.seur, features = markers.mig, group.by = "FB.info",
                         cols = c("midnightblue","darkorange1")) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1))#+ scale_y_discrete(limits=rev)
```

```{r fig.width=9,fig.height=6}
VlnPlot(GEX.seur, features = c("tdTomato-head","tdTomato-mid","tdTomato-tail","CreERT2"),
        group.by = "FB.info", ncol = 2)
```



```{r fig.width=9,fig.height=5.4}
DotPlot(GEX.seur, features = markers.mig, group.by = "seurat_clusters",
                         cols = c("midnightblue","darkorange1")) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1))#+ scale_y_discrete(limits=rev)
```


### sort             


```{r}
GEX.seur$sort_clusters <- factor(as.character(GEX.seur$seurat_clusters),
                                 levels = c(3,4,6,5,7,11,12,10,
                                            9,
                                            1,0,2,8))
```


```{r fig.width=5.4, fig.height=4}
cowplot::plot_grid(
pheatmap::pheatmap(table(FB.info=GEX.seur$FB.info,
      clusters=GEX.seur$sort_clusters)[c(3:5,10:12),],
                   main = "Cell Count",
                   gaps_row = c(3),
      #gaps_col = c(12,13,14),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.0f", legend = F, silent = T)$gtable,

pheatmap::pheatmap(100*rowRatio(table(FB.info=GEX.seur$FB.info,
                                clusters=GEX.seur$sort_clusters)[c(3:5,10:12),]),
                   main = "Cell Ratio",
                   gaps_row = c(3),
      #gaps_col = c(12,13,14),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.1f", legend = F, silent =T)$gtable,
ncol = 1)
```

### markers       


```{r message=FALSE, warning=FALSE, paged.print=TRUE}
# find markers for every cluster compared to all remaining cells, report only the positive ones
Idents(GEX.seur) <- "sort_clusters"

#GEX.markers.pre <- FindAllMarkers(GEX.seur, only.pos = TRUE, 
#                                  min.pct = 0.05,
#                                  test.use = "MAST",
#                                  logfc.threshold = 0.25)
GEX.markers.pre <- read.table("sc10x_LYN.marker.subset1_sort1007.csv", header = TRUE, sep = ",")
GEX.markers.pre %>% group_by(cluster) %>% top_n(n = 8, wt = avg_log2FC)
```


```{r eval=FALSE, include=FALSE}
write.table(GEX.markers.pre, 
            "sc10x_LYN.marker.subset1_sort1007.csv", 
            col.names = TRUE,
            row.names = FALSE,
            quote = F,
            sep = ",")
```


```{r}
GEX.markers.sort <- GEX.markers.pre
GEX.markers.sort$cluster <- factor(as.character(GEX.markers.sort$cluster),
                          levels = levels(GEX.seur$sort_clusters))


markers.pre_t48 <- (GEX.markers.sort %>% group_by(cluster) %>% 
                  filter(pct.1>0.1) %>%
                   top_n(n = 48, wt = avg_log2FC) %>%
                   ungroup() %>%
  arrange(desc(avg_log2FC*pct.1),gene) %>%
                             distinct(gene, .keep_all = TRUE) %>%
                             arrange(cluster,p_val_adj))$gene

markers.pre_t60 <- (GEX.markers.sort %>% group_by(cluster) %>% 
                  filter(pct.1>0.1 & gene %in% grep("Rps|Rpl",GEX.markers.sort$gene,invert = T,value = T)) %>%
                   top_n(n = 60, wt = avg_log2FC) %>%
                   ungroup() %>%
  arrange(desc(avg_log2FC*pct.1),gene) %>%
                             distinct(gene, .keep_all = TRUE) %>%
                             arrange(cluster,p_val_adj))$gene

markers.pre_t120 <- (GEX.markers.sort %>% group_by(cluster) %>% 
                  filter(pct.1>0.1 & gene %in% grep("Rps|Rpl",GEX.markers.sort$gene,invert = T,value = T)) %>%
                   top_n(n = 120, wt = avg_log2FC) %>%
                   ungroup() %>%
  arrange(desc(avg_log2FC*pct.1),gene) %>%
                             distinct(gene, .keep_all = TRUE) %>%
                             arrange(cluster,p_val_adj))$gene
```


```{r fig.width=7.6, fig.height=9.6}
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t60[1:64]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t60[65:128]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t60[129:192]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t60[193:256]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t60[257:320]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t60[321:384]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t60[385:448]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t60[449:495]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))

```


```{r eval=FALSE, fig.height=9.6, fig.width=7.6, include=FALSE}
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[1:64]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[65:128]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[129:192]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[193:256]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[257:320]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[321:384]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[385:448]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[449:512]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[513:576]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[577:640]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[641:704]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[705:772]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[773:836]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "sort_clusters", features = rev(markers.pre_t120[837:870]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
```


```{r}
GEX.seur$cnt <- factor(as.character(GEX.seur$FB.info),
                       levels = levels(GEX.seur$FB.info)[c(12:10,5:3)])
color.cnt <- rev(color.FB1)
```



## signature score             


```{r}

#### 10x data, calculate signature score       
#
## The code below is from Adam Hamber
## 2D scoring by Itay
get_controls <- function(counts, gene.list, verbose=F, control.genes.per.gene=10)
{
    # Itay: "Such scores are inevitably correlated with cell complexity so to avoid 
    # that I subtract a "control" score which is generated by averaging over a control 
    # gene set. Control gene sets are chosen to contain 100 times more genes than the 
    # real gene set (analogous to averaging over 100 control sets of similar size) and 
    # to have the same distribution of population/bulk - based expression levels as the 
    # real gene set, such that they are expected to have the same number of "zeros" and 
    # to eliminate the correlation with complexity."
    # ---------------------------------------------------------------------------------
    # Going to find control points by finding the closest genes in terms of expression level and % of the time we observe it
    if(verbose){cat(sprintf("Finding %s background genes based on similarity to given gene set [%s genes] \n", 
                            control.genes.per.gene*length(gene.list), length(gene.list)))}
    cat("Summarizing data \n")
    summary = data.frame(gene=row.names(counts), mean.expr = Matrix::rowMeans(counts), fract.zero = Matrix::rowMeans(counts==0), stringsAsFactors = F)
    #summary = data.frame(gene=row.names(counts), mean.expr = apply(counts,1,mean), fract.zero = apply(counts==0,1,mean), stringsAsFactors = F)
    summary$mean.expr.s = scale(summary$mean.expr)
    summary$fract.zero.s = scale(summary$fract.zero)
    actual.genes = summary[summary$gene %in% gene.list,]
    background.genes = summary[!summary$gene %in% gene.list,]
    
    #find the 10 closest genes to each cell cycle marker gene and add them to the lists of control genes
    get_closest_genes <- function(i)
    {
        background.genes$dist = sqrt((background.genes$mean.expr.s - actual.genes$mean.expr.s[i])^2 + 
                                         (background.genes$fract.zero.s - actual.genes$fract.zero.s[i])^2)
        ordered = background.genes$gene[order(background.genes$dist)]
        ordered = ordered[!ordered %in% controls] # don't take genes that already appear in the list 
        closest = head(ordered, n=control.genes.per.gene)
        return(closest)
    }
    controls = c();
    
    for (i in 1:length(gene.list)){
        #info(sprintf("Finding %s control genes for %s", control.genes.per.gene, gene.list[i]))
        closest = get_closest_genes(i)
        #info(sprintf("Found %s: ", length(closest)))
        controls = unique(c(controls, closest))
    }
    
    if(verbose){cat(sprintf("Control gene selection complete. %s genes found. \n", length(controls)))}
    #print(controls)
    return(controls)
}

## Define calculate function
calculate_signature_score <- function(count_matrix, gene_list){
    control_gene <- get_controls(counts = count_matrix,
                                 gene.list = gene_list)
    signature_score <- colMeans(count_matrix[gene_list, ], na.rm = TRUE) - 
        colMeans(count_matrix[control_gene, ], na.rm = TRUE)
    return(signature_score)
}

add_geneset_score <- function(obj, geneset, setname){
  score <- calculate_signature_score(as.data.frame(obj@assays[['RNA']]@data),
                                     geneset)
  obj <- AddMetaData(obj,
                     score,
                     setname)
  return(obj)
}
```


```{r}
## proc_DEG()
#       to process edgeR result for DEGs' comparison
#              mat_cut is a matrix after advanced filtering, 'like TPM > n in at least one condition'
# 

proc_DEG <- function(deg, p.cut=0.05, FC.cut = 2, padj=TRUE, abs=TRUE, mat_cut=NULL, gene_cut=NULL){
    rownames(deg) <- deg$gene
    
    if(padj==TRUE){
        deg <- deg %>% filter(padj < p.cut)
    }else{
        deg <- deg %>% filter(pvalue < p.cut)
    }
    
    if(abs==TRUE){
        deg <- deg %>% filter(abs(FC) > FC.cut)
    }else if(FC.cut >0){
        deg <- deg %>% filter(FC > FC.cut)
    }else{
        deg <- deg %>% filter(FC < FC.cut)
    }
    
    if(!is.null(mat_cut)){
        deg <- deg[rownames(deg) %in% rownames(mat_cut),]
    }
    if(!is.null(gene_cut)){
        deg <- deg[rownames(deg) %in% gene_cut,]
    }
    return(deg)
}
```


### DAM sig            

DAM signature expression as feature plot (try top 50, top100, top250, top500)        

```{r}
DAM.sig <- read.csv("../../../20230811_10x_LYN/analysis_plus_exogene/figures1002/new/ranking_of_DAM_indicator_genes.csv")
DAM.sig[1:8,]
```

```{r}
DAM.list <- list(top50=DAM.sig$Gene[1:50],
                 top100=DAM.sig$Gene[1:100],
                 top250=DAM.sig$Gene[1:250],
                 top500=DAM.sig$Gene[1:500])
```


```{r}
DAM.list
```


```{r}
lapply(DAM.list, length)
```


```{r}
GEX.seur <- add_geneset_score(GEX.seur, DAM.list$top50, "DAM.sig_top50")
GEX.seur <- add_geneset_score(GEX.seur, DAM.list$top100, "DAM.sig_top100")
GEX.seur <- add_geneset_score(GEX.seur, DAM.list$top250, "DAM.sig_top250")
GEX.seur <- add_geneset_score(GEX.seur, DAM.list$top500, "DAM.sig_top500")
```

```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
ppnew.2.v1 <- VlnPlot(GEX.seur, features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), 
                      group.by = "cnt", cols = color.cnt,
                      ncol = 2, pt.size = 0, raster = F) & geom_jitter(alpha=0.15, shape=16, width = 0.2, size = 0.02)
ppnew.2.v1
```


```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
ppnew.2.v1 <- VlnPlot(GEX.seur, features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), 
                      same.y.lims = T,
                      group.by = "cnt", cols = color.cnt,
                      ncol = 2, pt.size = 0, raster = F) & 
    geom_boxplot(outlier.size = 0, fill="white", width=0.2, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=3, color="black", alpha=0.55) &
  ggpubr::stat_compare_means(aes(lable = ..p.signif..), 
                               method = "wilcox.test",
                               comparisons = list(c("P06.CTR","P06.MIG"),
                                                  c("P06.MIG","P06.TDT"),
                                                  c("P06.CTR","P06.TDT"),
                                                  c("P30.PBS.CTR","P30.PBS.MIG"),
                                                  c("P30.PBS.MIG","P30.PBS.TDT"),
                                                  c("P30.PBS.CTR","P30.PBS.TDT"),
                                                  c("P06.TDT","P30.PBS.TDT")),
                               label.y = c(0.55,0.75,0.95,0.55,0.75,0.95,1.1),
                               size=3
                               )
ppnew.2.v1
```


```{r fig.width=12, fig.height=2.5}
ppnew.2a <- FeaturePlot(GEX.seur,features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), ncol = 4,
                        raster = T, pt.size = 3.5,
            keep.scale = "all")
ppnew.2a
```

```{r fig.height=2.5, fig.width=12, message=FALSE, warning=FALSE}
mapal <- colorRampPalette(RColorBrewer::brewer.pal(4,"Spectral"))(120)
ppnew.2d <- FeaturePlot(GEX.seur,features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), ncol = 4,
                        raster = T, pt.size = 3.5,
            keep.scale = "all") & scale_color_gradientn(colors = rev(mapal))
ppnew.2d
```


```{r}
#saveRDS(GEX.seur, "Spp1tdt.subset1_P06_P30PBS.sort1007.rds")
```


## subset1 DEGs                      


```{r}
GEX.comp <- GEX.seur
Idents(GEX.comp) <- "cnt"
```


```{r}
GEX.comp
```

```{r}
GEX.comp$cnt[1:5]
```


```{r}
DEGs.a <- list()


for(mm in c("P06","P30.PBS")){
  for(nn in c("CTR","MIG")){
    DEGs.a[[paste0(mm,".TDTvs",nn)]] <- FindAllMarkers(subset(GEX.comp, subset = cnt %in% c(paste0(mm,".",nn),paste0(mm,".TDT")) & age %in% c(mm)),
                                                       assay = "RNA",
                                                       only.pos = T,
                                                       min.pct = 0.05, 
                                                       logfc.threshold = 0.1,
                                                       test.use = "MAST")
    
     
  }
}

```


```{r}
#DEGs.a
```

```{r}
names(DEGs.a)
```


```{r}
# save DEGs' table
df.DEGs.a <- data.frame()

for(nn in names(DEGs.a)){
  df.DEGs.a <- rbind(df.DEGs.a, data.frame(DEGs.a[[nn]], contrast = nn))
}

#write.csv(df.DEGs.a, "DEGs.subset1.csv")
```


### DEG stat              

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
cut.padj = 0.05
cut.log2FC = 0.3   
  
cut.pct1 = 0.05

df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  summarise(up.DEGs = n()) %>% as.data.frame()
  
```

```{r}
pp.stat.DEG <- list()
```


```{r}
df.DEGs.a$cluster <- factor(as.character(df.DEGs.a$cluster),
                            levels = levels(GEX.seur$cnt))
```


```{r message=FALSE, warning=FALSE}
pp.stat.DEG[["a"]] <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  summarise(up.DEGs = n()) %>% as.data.frame() %>%
  ggplot(aes(x=contrast, y=up.DEGs, color = cluster)) +
  geom_bar(stat="summary", fun="mean", position = position_dodge(0.75), width = 0.58, fill="white") +
  geom_text(aes(label = up.DEGs),vjust=-0.21, show.legend = F, position = position_dodge(0.75) ) +
  theme_classic(base_size = 15) +
  scale_color_manual(values = color.cnt, name="") +
  labs(title=paste0("up.DEGs stat, pct.1>0.05, padj<",cut.padj,", |log2FC|>",cut.log2FC), y = "Number of DEGs") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6),
        title =element_text(size=12, face='bold'))
pp.stat.DEG[["a"]]
```


```{r message=FALSE, warning=FALSE, paged.print=FALSE}
cut.padj = 0.05
cut.log2FC = 0.1   
  
cut.pct1 = 0.05

df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  summarise(up.DEGs = n()) %>% as.data.frame()
  
```

```{r message=FALSE, warning=FALSE}
pp.stat.DEG[["a"]] <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  summarise(up.DEGs = n()) %>% as.data.frame() %>%
  ggplot(aes(x=contrast, y=up.DEGs, color = cluster)) +
  geom_bar(stat="summary", fun="mean", position = position_dodge(0.75), width = 0.58, fill="white") +
  geom_text(aes(label = up.DEGs),vjust=-0.21, show.legend = F, position = position_dodge(0.75) ) +
  theme_classic(base_size = 15) +
  scale_color_manual(values = color.cnt, name="") +
  labs(title=paste0("up.DEGs stat, pct.1>0.05, padj<",cut.padj,", |log2FC|>",cut.log2FC), y = "Number of DEGs") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6),
        title =element_text(size=12, face='bold'))
pp.stat.DEG[["a"]]
```

### DEG plot             


```{r}
pp.DEGs.a <- lapply(DEGs.a, function(x){NA})
```

```{r}
names(DEGs.a)
```


```{r}
DEGs.a.combine <- DEGs.a
DEGs.a.combine <- lapply(DEGs.a.combine, function(x){
  for(zz in c("P06.MIG","P06.CTR","P30.PBS.MIG","P30.PBS.CTR")){
    x[x$cluster==zz,"avg_log2FC"] <- -x[x$cluster==zz,"avg_log2FC"]
  }
  
  x
})

```


```{r fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
pp.DEGs.a$P06.TDTvsCTR <- DEGs.a.combine$P06.TDTvsCTR %>%
  mutate(label=ifelse(((p_val_adj < 1e-8 & avg_log2FC<0) | (p_val_adj < 1e-8 & avg_log2FC>0) | (p_val_adj < 0.05 & abs(avg_log2FC) > 0.5)) &
                        !grepl("^Gm|^Hsp|^Rps|^Rpl|Rik$|Xist|Tsix|Uty|Ddx3y|Eif2s3y|Kdm5d",gene),gene,""),
         sig.=ifelse(p_val_adj<0.05 & avg_log2FC<0,"CTR",ifelse(p_val_adj<0.05 & avg_log2FC>0,"TDT","None")),
         padj=ifelse(p_val_adj<1e-60,p_val_adj+1e-60,p_val_adj)) %>%
  ggplot(aes(y= -log10(padj), x=avg_log2FC, size=pct.1, label=label,fill=sig.)) +
  geom_point(shape=21, alpha=0.65) +
  geom_text_repel(size=2.5, max.overlaps = 500) +
  scale_fill_manual(values = c("CTR"="Skyblue",
                               "TDT"="pink",
                               "None"="grey")) +
  theme_classic() + labs(title="P06, TDT vs CTR") +
  guides(size = guide_legend(order = 2), fill=guide_legend(order = 1, reverse = F)) +
  geom_vline(xintercept = c(-0.1,0.1), linetype="dotted") + xlim(c(-1,2))
pp.DEGs.a$P06.TDTvsCTR
```


```{r fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
pp.DEGs.a$P06.TDTvsMIG <- DEGs.a.combine$P06.TDTvsMIG %>%
  mutate(label=ifelse(((p_val_adj < 1e-5 & avg_log2FC<0) | (p_val_adj < 1e-5 & avg_log2FC>0) | (p_val_adj < 0.05 & abs(avg_log2FC) > 0.5)) &
                        !grepl("^Gm|^Hsp|^Rps|^Rpl|Rik$|Xist|Tsix|Uty|Ddx3y|Eif2s3y|Kdm5d",gene),gene,""),
         sig.=ifelse(p_val_adj<0.05 & avg_log2FC<0,"MIG",ifelse(p_val_adj<0.05 & avg_log2FC>0,"TDT","None")),
         padj=ifelse(p_val_adj<1e-60,p_val_adj+1e-60,p_val_adj)) %>%
  ggplot(aes(y= -log10(padj), x=avg_log2FC, size=pct.1, label=label,fill=sig.)) +
  geom_point(shape=21, alpha=0.65) +
  geom_text_repel(size=2.5, max.overlaps = 500) +
  scale_fill_manual(values = c("MIG"="Skyblue",
                               "TDT"="pink",
                               "None"="grey")) +
  theme_classic() + labs(title="P06, TDT vs MIG") +
  guides(size = guide_legend(order = 2), fill=guide_legend(order = 1, reverse = F)) +
  geom_vline(xintercept = c(-0.1,0.1), linetype="dotted") + xlim(c(-1,1))
pp.DEGs.a$P06.TDTvsMIG
```


```{r fig.width=12, fig.height=6}
pp.DEGs.a$P30.PBS.TDTvsCTR <- DEGs.a.combine$P30.PBS.TDTvsCTR %>%
  mutate(label=ifelse(((p_val_adj < 1e-3 & avg_log2FC<0) | (p_val_adj < 1e-3 & avg_log2FC>0) | (p_val_adj < 0.05 & abs(avg_log2FC) > 0.5)) &
                        !grepl("^Gm|^Hsp|^Rps|^Rpl|Rik$|Xist|Tsix|Uty|Ddx3y|Eif2s3y|Kdm5d",gene),gene,""),
         sig.=ifelse(p_val_adj<0.05 & avg_log2FC<0,"CTR",ifelse(p_val_adj<0.05 & avg_log2FC>0,"TDT","None")),
         padj=ifelse(p_val_adj<1e-60,p_val_adj+1e-60,p_val_adj)) %>%
  ggplot(aes(y= -log10(padj), x=avg_log2FC, size=pct.1, label=label,fill=sig.)) +
  geom_point(shape=21, alpha=0.65) +
  geom_text_repel(size=2.5, max.overlaps = 500) +
  scale_fill_manual(values = c("CTR"="Skyblue",
                               "TDT"="pink",
                               "None"="grey")) +
  theme_classic() + labs(title="P30.PBS, TDT vs CTR") +
  guides(size = guide_legend(order = 2), fill=guide_legend(order = 1, reverse = F)) +
  geom_vline(xintercept = c(-0.1,0.1), linetype="dotted") #+ xlim(c(-1,2))
pp.DEGs.a$P30.PBS.TDTvsCTR
```


```{r fig.width=12, fig.height=6}
pp.DEGs.a$P30.PBS.TDTvsMIG <- DEGs.a.combine$P30.PBS.TDTvsMIG %>%
  mutate(label=ifelse(((p_val_adj < 1e-3 & avg_log2FC<0) | (p_val_adj < 1e-3 & avg_log2FC>0) | (p_val_adj < 0.05 & abs(avg_log2FC) > 0.5)) &
                        !grepl("^Gm|^Hsp|^Rps|^Rpl|Rik$|Xist|Tsix|Uty|Ddx3y|Eif2s3y|Kdm5d",gene),gene,""),
         sig.=ifelse(p_val_adj<0.05 & avg_log2FC<0,"MIG",ifelse(p_val_adj<0.05 & avg_log2FC>0,"TDT","None")),
         padj=ifelse(p_val_adj<1e-60,p_val_adj+1e-60,p_val_adj)) %>%
  ggplot(aes(y= -log10(padj), x=avg_log2FC, size=pct.1, label=label,fill=sig.)) +
  geom_point(shape=21, alpha=0.65) +
  geom_text_repel(size=2.5, max.overlaps = 500) +
  scale_fill_manual(values = c("MIG"="Skyblue",
                               "TDT"="pink",
                               "None"="grey")) +
  theme_classic() + labs(title="P30.PBS, TDT vs MIG") +
  guides(size = guide_legend(order = 2), fill=guide_legend(order = 1, reverse = F)) +
  geom_vline(xintercept = c(-0.1,0.1), linetype="dotted") #+ xlim(c(-1,2))
pp.DEGs.a$P30.PBS.TDTvsMIG
```


## new clusters             
       
      
```{r}
GEX.seur$new_clusters <- as.character(GEX.seur$seurat_clusters)

GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(4)] <- "C1"
GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(3,6)] <- "C2"
GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(5)] <- "C3"
GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(7)] <- "C4"
GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(11)] <- "C5"
GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(12)] <- "C6"
GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(10)] <- "C7"
GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(9)] <- "C8"
GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(0)] <- "C9"
GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(1,2)] <- "C10"
GEX.seur$new_clusters[GEX.seur$new_clusters %in% c(8)] <- "C11"

GEX.seur$new_clusters <- factor(GEX.seur$new_clusters,
                                paste0("C",1:11))
```


```{r paged.print=FALSE}
head(GEX.seur@meta.data)
```
      
```{r}
#
GEX.seur$age1 <- factor(as.character(GEX.seur$age),
                        levels = c("P30.PBS","P06"))

#
GEX.seur$FB.new <- factor(as.character(GEX.seur$FB.info),
                          levels = rev(levels(GEX.seur$FB.info))[c(1:3,8:10)])

color.FBnew <- rev(color.FB1)
```

   

### new markers                

```{r message=FALSE, warning=FALSE, paged.print=TRUE}
# find markers for every cluster compared to all remaining cells, report only the positive ones
Idents(GEX.seur) <- "new_clusters"

#GEX.markers.new <- FindAllMarkers(GEX.seur, only.pos = TRUE, 
#                                  min.pct = 0.05,
#                                  test.use = "MAST",
#                                  logfc.threshold = 0.25)
GEX.markers.new <- read.table("sc10x_LYN.0921.marker.subset1_new.csv", header = TRUE, sep = ",")
GEX.markers.new %>% group_by(cluster) %>% top_n(n = 8, wt = avg_log2FC)
```


```{r eval=FALSE, include=FALSE}
write.table(GEX.markers.new, 
            "sc10x_LYN.0921.marker.subset1_new.csv", 
            col.names = TRUE,
            row.names = FALSE,
            quote = F,
            sep = ",")
```   
    
      
```{r}
markers.new <- GEX.markers.new
markers.new$cluster <- factor(as.character(GEX.markers.new$cluster),
                               levels = levels(GEX.seur$new_clusters))

markers.new_t60 <- (markers.new %>% group_by(cluster) %>% 
                  filter(pct.1>0.1 & gene %in% grep("Rps|Rpl|Gm|Rik$|Xist|Tsix",markers.new$gene,invert = T,value = T)) %>%
                   top_n(n = 60, wt = avg_log2FC) %>%
                   ungroup() %>%
  #arrange(desc(avg_log2FC*pct.1),gene) %>%
    arrange(desc(pct.1),gene) %>%
                             distinct(gene, .keep_all = TRUE) %>%
                             arrange(cluster,p_val_adj))$gene
```
      
      
```{r fig.width=7.6, fig.height=9.6}
DotPlot(GEX.seur, group.by = "new_clusters", features = rev(markers.new_t60[1:64]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "new_clusters", features = rev(markers.new_t60[65:128]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "new_clusters", features = rev(markers.new_t60[129:192]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "new_clusters", features = rev(markers.new_t60[193:256]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "new_clusters", features = rev(markers.new_t60[257:320]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "new_clusters", features = rev(markers.new_t60[321:384]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))
DotPlot(GEX.seur, group.by = "new_clusters", features = rev(markers.new_t60[385:457]))  + coord_flip() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6))

```   
      
      
      
      
### plot1                    

umap in clusters      

```{r fig.width=11,fig.height=4.5}
pp.umap.1a <- DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "seurat_clusters", raster = F, pt.size = 0.3
                      ) +
           DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "FB.new", cols = color.FBnew, raster = F, pt.size = 0.3
                   )
pp.umap.1a
```

```{r fig.width=11.2,fig.height=4.5}
pp.umap.1b <- DimPlot(GEX.seur, reduction = "umap", label = T, group.by = "new_clusters", repel = F, raster = F, pt.size = 0.3
                      ) +
           DimPlot(GEX.seur, reduction = "umap", label = F, group.by = "FB.new", cols = color.FBnew, raster = F, pt.size = 0.3
                   )
pp.umap.1b
```

```{r eval=FALSE, include=FALSE}
ggsave("./figure1008/subset1.plot1.umap.a.big.pdf",
       width = 11,height = 4.5,
       plot = pp.umap.1a) 
ggsave("./figure1008/subset1.plot1.umap.b.big.pdf",
       width = 11.2,height = 4.5,
       plot = pp.umap.1b) 
```


### plot2        


```{r  fig.width=9.8, fig.height=6.4}
pp.umap.2a <- DimPlot(GEX.seur, label = F,  repel = F, reduction = 'umap', group.by = "FB.new", split.by = "FB.new", raster = F, pt.size = 0.3,
        ncol = 3, cols = color.FBnew)
pp.umap.2a
``` 


```{r  fig.width=8.5, fig.height=4.4}
pp.umap.2b <- DimPlot(GEX.seur, label = F,repel = F, reduction = 'umap', group.by = "FB.new", split.by = "age", 
                     raster = F, pt.size = 0.3,
                     ncol = 3, cols = color.FBnew)
pp.umap.2b
``` 


```{r  fig.width=9.4, fig.height=6.4}
pp.umap.2c <- DimPlot(GEX.seur, label = F,  repel = F, reduction = 'umap', group.by = "new_clusters", split.by = "FB.new", raster = F, pt.size = 0.3,
        ncol = 3)
pp.umap.2c
``` 



```{r  fig.width=8, fig.height=4.4}
pp.umap.2d <- DimPlot(GEX.seur, label = F,repel = F, reduction = 'umap', group.by = "new_clusters", split.by = "age", 
                     raster = F, pt.size = 0.3,
                     ncol = 3)
pp.umap.2d
``` 


```{r eval=FALSE, include=FALSE}
ggsave("./figure1008/subset1.plot2.umap.a.big.pdf",
       width = 9.8,height = 6.4,
       plot = pp.umap.2a) 
ggsave("./figure1008/subset1.plot2.umap.b.big.pdf",
       width = 8.5,height = 4.4,
       plot = pp.umap.2b) 

ggsave("./figure1008/subset1.plot2.umap.c.big.pdf",
       width = 9.4,height = 6.4,
       plot = pp.umap.2c) 
ggsave("./figure1008/subset1.plot2.umap.d.big.pdf",
       width = 8,height = 4.4,
       plot = pp.umap.2d) 
```


### plot3            


composition              


```{r fig.width=5.4, fig.height=4}
pp.comp.3a <- cowplot::plot_grid(
pheatmap::pheatmap(table(FB.info=GEX.seur$FB.new,
      clusters=GEX.seur$new_clusters),
                   main = "Cell Count",
                   gaps_row = c(3),
      #gaps_col = c(12,13,14),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.0f", legend = F, silent = T)$gtable,

pheatmap::pheatmap(100*rowRatio(table(FB.info=GEX.seur$FB.new,
                                clusters=GEX.seur$new_clusters)),
                   main = "Cell Ratio",
                   gaps_row = c(3),
      #gaps_col = c(12,13,14),
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.1f", legend = F, silent =T)$gtable,
ncol = 1)
pp.comp.3a
```


```{r eval=FALSE, include=FALSE}
ggsave("./figure1008/subset1.plot3.composition.a.pdf",
       width = 4.5,height = 4,
       plot = pp.comp.3a)
```


```{r}
stat_sort <- GEX.seur@meta.data[,c("FB.new","new_clusters")]
```


```{r}
stat_sort.s <- stat_sort %>%
  group_by(FB.new,new_clusters) %>%
  summarise(count=n()) %>%
  mutate(prop= count/sum(count)) %>%
  ungroup()
```

```{r}
dim(stat_sort.s)
#stat_sort.s
```


```{r eval=FALSE, include=FALSE, paged.print=FALSE}
write.csv(stat_sort.s %>% reshape2::recast(new_clusters ~ FB.new, measure.var = 3), 
          "figure1008/subset1.plot3.composition.new_clusters.count.csv")
write.csv(stat_sort.s %>% reshape2::recast(new_clusters ~ FB.new, measure.var = 4), 
          "figure1008/subset1.plot3.composition.new_clusters.ratio.csv")
```


```{r fig.height=4, fig.width=10} 
pp.comp.3b <- stat_sort.s %>% 
  ggplot(aes(x = new_clusters, y = 100*prop, color=FB.new)) +
  geom_bar(stat="summary", fun="mean", position = position_dodge(0.75), width = 0.58, fill="white") +
  theme_classic(base_size = 15) + 
  scale_color_manual(values = color.FBnew, name="") +
  labs(title="Cell Composition", y="Proportion") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6)) +
  
  geom_point(aes(x = new_clusters, y = 100*prop, color=FB.new),
             position = position_dodge(0.75),
             shape=16,alpha=0.75,size=1.75,
             stroke=0.15, show.legend = F)
pp.comp.3b
```

```{r eval=FALSE, include=FALSE}
ggsave("./figure1008/subset1.plot3.composition.b.pdf",
       width = 10,height = 4,
       plot = pp.comp.3b)
```



### plot4            


```{r}
final.markers <- c("Apoe","Ms4a6d","Ms4a6c","Apoc1",
                   "Apoc2","Fn1","Tspo","Ctss",
                   "Ctsc","Ctsd","Igf1","Sparc",
                   "Siglech","P2ry12","P2ry13","Tmem119",
                   "Sall1","Slc2a5","Gpr34","Maf")
```


```{r}
length(final.markers)
sum(final.markers %in% markers.new$gene)
```

```{r}
final.markers.sort <- (markers.new %>% group_by(cluster) %>%
                         filter(gene %in% final.markers) %>%
                         ungroup() %>%
                         arrange(desc(avg_log2FC*pct.1),gene) %>%
                         distinct(gene, .keep_all = TRUE) %>%
                         arrange(cluster, p_val_adj))$gene
final.markers.sort
```

```{r}
setdiff(final.markers,final.markers.sort)
```

```{r}
final.markers.new <- c(final.markers.sort[1:14],"Maf",final.markers.sort[15:19])
mapal <- colorRampPalette(RColorBrewer::brewer.pal(4,"Spectral"))(120)
```


```{r fig.width=8.7,fig.height=4.2}
pp.dot.4a1 <- DotPlot(GEX.seur, features = final.markers, group.by = "new_clusters"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters")
pp.dot.4a1
```


```{r fig.width=8.7,fig.height=4.2}
pp.dot.4a1 <- DotPlot(GEX.seur, features = final.markers.sort, group.by = "new_clusters"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters")
pp.dot.4a1
```


```{r fig.width=6.9,fig.height=3.5}
pp.dot.4a1 <- DotPlot(GEX.seur, features = final.markers.new, group.by = "new_clusters"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters")
pp.dot.4a1
```


```{r fig.width=6.9,fig.height=3.5, message=FALSE}
pp.dot.4a2 <- DotPlot(GEX.seur, features = final.markers.new, group.by = "new_clusters"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters")  +
  scale_color_gradientn(colours  = rev(mapal))
pp.dot.4a2
```




```{r fig.width=7.2,fig.height=3}
pp.dot.4b1 <- DotPlot(GEX.seur, features = final.markers.new, group.by = "FB.new"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Conditions")
pp.dot.4b1
```


```{r fig.height=3, fig.width=7.2, message=FALSE}
pp.dot.4b2 <- DotPlot(GEX.seur, features = final.markers.new, group.by = "FB.new"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Conditions")  +
  scale_color_gradientn(colours  = rev(mapal))
pp.dot.4b2
```


```{r}
levels.cluster_cnt <- as.vector(unlist(sapply(levels(GEX.seur$new_clusters),function(x){
                         paste0(x,"_",levels(GEX.seur$FB.new))
                      })))
levels.cluster_cnt
```


```{r}
GEX.seur$cluster_cnt <- factor(paste0(as.character(GEX.seur$new_clusters),
                                      "_",
                                      as.character(GEX.seur$FB.new)),
                               levels = levels.cluster_cnt)

```



```{r fig.width=6.9,fig.height=10.5}
pp.dot.4c1 <- DotPlot(GEX.seur, features = final.markers.new, group.by = "cluster_cnt"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters_Conditions")
pp.dot.4c1
```


```{r fig.width=7.2,fig.height=6}
pp.dot.4c1a <- DotPlot(subset(GEX.seur,subset= age %in% c("P06") & new_clusters %in% paste0("C",1:8)), 
                       features = final.markers.new, group.by = "cluster_cnt"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters_Conditions")
pp.dot.4c1a
```


```{r fig.width=7.6,fig.height=4.5}
pp.dot.4c1b <- DotPlot(subset(GEX.seur,subset= age %in% c("P30.PBS") & new_clusters %in% paste0("C",8:11)), 
                       features = final.markers.new, group.by = "cluster_cnt"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters_Conditions")
pp.dot.4c1b
```


```{r fig.height=10.5, fig.width=6.9, message=FALSE}
pp.dot.4c2 <- DotPlot(GEX.seur, features = final.markers.new, group.by = "cluster_cnt"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters_Conditions")  +
  scale_color_gradientn(colours  = rev(mapal))
pp.dot.4c2
```


```{r fig.height=6, fig.width=7.2, message=FALSE}
pp.dot.4c2a <- DotPlot(subset(GEX.seur,subset= age %in% c("P06") & new_clusters %in% paste0("C",1:8)), 
                       features = final.markers.new, group.by = "cluster_cnt"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters_Conditions") +
  scale_color_gradientn(colours  = rev(mapal))
pp.dot.4c2a
```


```{r fig.height=4.5, fig.width=7.6, message=FALSE}
pp.dot.4c2b <- DotPlot(subset(GEX.seur,subset= age %in% c("P30.PBS") & new_clusters %in% paste0("C",8:11)), 
                       features = final.markers.new, group.by = "cluster_cnt"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters_Conditions") +
  scale_color_gradientn(colours  = rev(mapal))
pp.dot.4c2b
```



```{r eval=FALSE, include=FALSE}
#
write.table(final.markers, "figure1008/subset1.plot4.check_markers.raw.txt", row.names = F, col.names = F, quote = F)
write.table(final.markers.new, "figure1008/subset1.plot4.check_markers.sort.txt", row.names = F, col.names = F, quote = F)

#
ggsave("figure1008/subset1.plot4.dotplot.a1.pdf",
       width = 7.2, height = 3.9,
       plot = pp.dot.4a1)
ggsave("figure1008/subset1.plot4.dotplot.a2.pdf",
       width = 7.2, height = 3.9,
       plot = pp.dot.4a2)

#
ggsave("figure1008/subset1.plot4.dotplot.b1.pdf",
       width = 7.6, height = 3,
       plot = pp.dot.4b1)
ggsave("figure1008/subset1.plot4.dotplot.b2.pdf",
       width = 7.6, height = 3,
       plot = pp.dot.4b2)

#
ggsave("figure1008/subset1.plot4.dotplot.c1_a.pdf",
       width = 7.5, height = 6,
       plot = pp.dot.4c1a)
ggsave("figure1008/subset1.plot4.dotplot.c1_b.pdf",
       width = 8.1, height = 4.5,
       plot = pp.dot.4c1b)

ggsave("figure1008/subset1.plot4.dotplot.c2_a.pdf",
       width = 7.5, height = 6,
       plot = pp.dot.4c2a)
ggsave("figure1008/subset1.plot4.dotplot.c2_b.pdf",
       width = 8.1, height = 4.5,
       plot = pp.dot.4c2b)

```


### plot5                        


violin using same markers in plot4                        


```{r fig.height=20, fig.width=9, message=FALSE, warning=FALSE}
pp.violin.5a1 <- VlnPlot(GEX.seur, features = final.markers.new, group.by = "new_clusters", 
                      ncol = 2, pt.size = 0, raster = F) & geom_jitter(alpha=0.15, shape=16, width = 0.2, size = 0.02)
pp.violin.5a1
```


```{r fig.height=20, fig.width=9, message=FALSE, warning=FALSE}
pp.violin.5a2 <- VlnPlot(GEX.seur, features = final.markers.new, group.by = "new_clusters", 
                      ncol = 2, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55)
pp.violin.5a2
```


```{r fig.height=26, fig.width=7.6, message=FALSE, warning=FALSE}
pp.violin.5b1 <- VlnPlot(GEX.seur, features = final.markers.new, group.by = "FB.new", cols = color.FBnew,
                      ncol = 2, pt.size = 0, raster = F) & geom_jitter(alpha=0.15, shape=16, width = 0.2, size = 0.02)
pp.violin.5b1
```


```{r fig.height=26, fig.width=7.6, message=FALSE, warning=FALSE}
pp.violin.5b2 <- VlnPlot(GEX.seur, features = final.markers.new, group.by = "FB.new", cols = color.FBnew,
                      ncol = 2, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55)
pp.violin.5b2
```


```{r fig.height=26, fig.width=7.6, message=FALSE, warning=FALSE}
pp.violin.5b3 <- VlnPlot(GEX.seur, features = final.markers.new, group.by = "FB.new", cols = color.FBnew,
                      ncol = 2, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55) & ylim(c(0,7.2)) &
  ggpubr::stat_compare_means(aes(lable = ..p.signif..), 
                               method = "wilcox.test",
                               comparisons = list(c("P06.CTR","P06.MIG"),
                                                  c("P06.MIG","P06.TDT"),
                                                  c("P06.CTR","P06.TDT"),
                                                  c("P30.PBS.CTR","P30.PBS.MIG"),
                                                  c("P30.PBS.MIG","P30.PBS.TDT"),
                                                  c("P30.PBS.CTR","P30.PBS.TDT"),
                                                  c("P06.TDT","P30.PBS.TDT")),
                               label.y = c(6.3,6.8,7.3,6.3,6.8,7.3,7.8)-1,
                               size=1.75
                               )
pp.violin.5b3
```


```{r fig.height=26, fig.width=11.5, message=FALSE, warning=FALSE}
pp.violin.5c1a <- VlnPlot(subset(GEX.seur,subset= age %in% c("P06") & new_clusters %in% paste0("C",1:8)), 
                          features = final.markers.new, group.by = "cluster_cnt", cols = rep(color.FBnew[1:3],8),
                      ncol = 2, pt.size = 0, raster = F) & geom_jitter(alpha=0.15, shape=16, width = 0.2, size = 0.02)
pp.violin.5c1a
```


```{r fig.height=29, fig.width=8.6, message=FALSE, warning=FALSE}
pp.violin.5c1b <- VlnPlot(subset(GEX.seur,subset= age %in% c("P30.PBS") & new_clusters %in% paste0("C",8:11)), 
                          features = final.markers.new, group.by = "cluster_cnt", cols = rep(color.FBnew[4:6],4),
                      ncol = 2, pt.size = 0, raster = F) & geom_jitter(alpha=0.15, shape=16, width = 0.2, size = 0.02)
pp.violin.5c1b
```



```{r fig.height=26, fig.width=11.5, message=FALSE, warning=FALSE}
pp.violin.5c2a <- VlnPlot(subset(GEX.seur,subset= age %in% c("P06") & new_clusters %in% paste0("C",1:8)), 
                          features = final.markers.new, group.by = "cluster_cnt", cols = rep(color.FBnew[1:3],8),
                      ncol = 2, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55)
pp.violin.5c2a
```


```{r fig.height=29, fig.width=8.6, message=FALSE, warning=FALSE}
pp.violin.5c2b <- VlnPlot(subset(GEX.seur,subset= age %in% c("P30.PBS") & new_clusters %in% paste0("C",8:11)), 
                          features = final.markers.new, group.by = "cluster_cnt", cols = rep(color.FBnew[4:6],4),
                      ncol = 2, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55)
pp.violin.5c2b
```



```{r}
contrast.a <- list(c("P06.CTR","P06.MIG"),
                   c("P06.MIG","P06.TDT"),
                   c("P06.CTR","P06.TDT"))

plot.contrast.a <- list()

for(XXX in paste0("C",1:8)){
  
  
  plot.contrast.a <- c(plot.contrast.a,
                       lapply(contrast.a, function(x){
                         paste0(XXX,
                                "_",
                                x)
                       }))
}

plot.labely.a <- rep(c(6.3,6.8,7.3),8)
#
length(plot.contrast.a)
plot.contrast.a[1:6]
```


```{r}
contrast.b <- list(c("P30.PBS.CTR","P30.PBS.MIG"),
                   c("P30.PBS.MIG","P30.PBS.TDT"),
                   c("P30.PBS.CTR","P30.PBS.TDT"))

plot.contrast.b <- list()

for(XXX in paste0("C",8:11)){
  
  
  plot.contrast.b <- c(plot.contrast.b,
                       lapply(contrast.b, function(x){
                         paste0(XXX,
                                "_",
                                x)
                       }))
}

plot.labely.b <- rep(c(6.3,6.8,7.3),4)
#
length(plot.contrast.b)
plot.contrast.b[1:6]
```



```{r fig.height=29, fig.width=11.5, message=FALSE, warning=FALSE}
pp.violin.5c3a <- VlnPlot(subset(GEX.seur,subset= age %in% c("P06") & new_clusters %in% paste0("C",1:8)), 
                          features = final.markers.new, group.by = "cluster_cnt", cols = rep(color.FBnew[1:3],8),
                      ncol = 2, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55) & ylim(c(0,6.8)) &
  ggpubr::stat_compare_means(aes(lable = ..p.signif..), 
                               method = "wilcox.test",
                               comparisons = plot.contrast.a,
                               label.y = plot.labely.a-1,
                               size=1.5
                               ) 
pp.violin.5c3a
```


```{r fig.height=32, fig.width=8.6, message=FALSE, warning=FALSE}
pp.violin.5c3b <- VlnPlot(subset(GEX.seur,subset= age %in% c("P30.PBS") & new_clusters %in% paste0("C",8:11)), 
                          features = final.markers.new, group.by = "cluster_cnt", cols = rep(color.FBnew[4:6],4),
                      ncol = 2, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55) & ylim(c(0,6.8)) &
  ggpubr::stat_compare_means(aes(lable = ..p.signif..), 
                               method = "wilcox.test",
                               comparisons = plot.contrast.b,
                               label.y = plot.labely.b-1,
                               size=1.75
                               )
pp.violin.5c3b
```



```{r eval=FALSE, include=FALSE}
#
ggsave("figure1008/subset1.plot5.violin.a.pdf",
       width = 9, height = 20,
       plot = pp.violin.5a2)

#
ggsave("figure1008/subset1.plot5.violin.b1.pdf",
       width = 7.6, height = 26,
       plot = pp.violin.5b2)
ggsave("figure1008/subset1.plot5.violin.b2.pdf",
       width = 7.6, height = 29,
       plot = pp.violin.5b3)

#
ggsave("figure1008/subset1.plot5.violin.c1a.pdf",
       width = 11.5, height = 26,
       plot = pp.violin.5c2a)
ggsave("figure1008/subset1.plot5.violin.c1b.pdf",
       width = 8.6, height = 29,
       plot = pp.violin.5c2b)

ggsave("figure1008/subset1.plot5.violin.c2a.pdf",
       width = 11.5, height = 29,
       plot = pp.violin.5c3a)
ggsave("figure1008/subset1.plot5.violin.c2b.pdf",
       width = 8.6, height = 32,
       plot = pp.violin.5c3b)

```



### plot6             

DAM score, using ready-plot above        


```{r fig.width=12.3, fig.height=2.5}
pp.feat.6a1 <- FeaturePlot(GEX.seur,features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), ncol = 4,
                           raster = T, pt.size = 3.5#,keep.scale = "all"
                           )
pp.feat.6a1
```

```{r fig.height=2.5, fig.width=12.3, message=FALSE, warning=FALSE}
mapal <- colorRampPalette(RColorBrewer::brewer.pal(4,"Spectral"))(120)
pp.feat.6a2 <- FeaturePlot(GEX.seur,features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), ncol = 4,
                        raster = T, pt.size = 3.5,
            keep.scale = "all") & scale_color_gradientn(colors = rev(mapal))
pp.feat.6a2
```


```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
pp.feat.6b1 <- VlnPlot(GEX.seur, features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), 
                      group.by = "cnt", cols = color.cnt,
                      ncol = 2, pt.size = 0, raster = F) & geom_jitter(alpha=0.15, shape=16, width = 0.2, size = 0.02)
pp.feat.6b1
```


```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
pp.feat.6b2 <- VlnPlot(GEX.seur, features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), 
                      same.y.lims = T,
                      group.by = "cnt", cols = color.cnt,
                      ncol = 2, pt.size = 0, raster = F) & 
    geom_boxplot(outlier.size = 0, fill="white", width=0.2, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=3, color="black", alpha=0.55) & 
  ggpubr::stat_compare_means(aes(lable = ..p.signif..), 
                               method = "wilcox.test",
                               comparisons = list(c("P06.CTR","P06.MIG"),
                                                  c("P06.MIG","P06.TDT"),
                                                  c("P06.CTR","P06.TDT"),
                                                  c("P30.PBS.CTR","P30.PBS.MIG"),
                                                  c("P30.PBS.MIG","P30.PBS.TDT"),
                                                  c("P30.PBS.CTR","P30.PBS.TDT"),
                                                  c("P06.TDT","P30.PBS.TDT")),
                               label.y = c(0.6,0.75,0.9,0.6,0.75,0.9,1.05),
                               size=2.35
                               )
pp.feat.6b2
```


```{r fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
pp.feat.6c1 <- VlnPlot(GEX.seur, features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), 
                      group.by = "new_clusters", #cols = color.cnt,
                      ncol = 2, pt.size = 0, raster = F) & geom_jitter(alpha=0.15, shape=16, width = 0.2, size = 0.02)
pp.feat.6c1
```


```{r fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
pp.feat.6c2 <- VlnPlot(GEX.seur, features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), 
                      group.by = "new_clusters", #cols = color.cnt,
                      ncol = 2, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.2, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=3, color="black", alpha=0.55)
pp.feat.6c2
```


```{r fig.height=5.8, fig.width=12.5, message=FALSE, warning=FALSE}
pp.feat.6c3a <- VlnPlot(subset(GEX.seur,subset= age %in% c("P06") & new_clusters %in% paste0("C",1:8)), 
                          features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), 
                        group.by = "cluster_cnt", cols = rep(color.FBnew[1:3],8),
                      ncol = 2, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55) & ylim(c(-0.25,0.88)) &
  ggpubr::stat_compare_means(aes(lable = ..p.signif..), 
                               method = "wilcox.test",
                               comparisons = plot.contrast.a,
                               label.y = (plot.labely.a-1)/8,
                               size=1.5
                               ) 
pp.feat.6c3a
```


```{r fig.height=8, fig.width=8.6, message=FALSE, warning=FALSE}
pp.feat.6c3b <- VlnPlot(subset(GEX.seur,subset= age %in% c("P30.PBS") & new_clusters %in% paste0("C",8:11)), 
                          features = c("DAM.sig_top50","DAM.sig_top100","DAM.sig_top250","DAM.sig_top500"), 
                        group.by = "cluster_cnt", cols = rep(color.FBnew[4:6],4),
                      ncol = 2, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55) & ylim(c(-0.25,0.9)) &
  ggpubr::stat_compare_means(aes(lable = ..p.signif..), 
                               method = "wilcox.test",
                               comparisons = plot.contrast.b,
                               label.y = (plot.labely.b-1)/7.5,
                               size=1.75
                               )
pp.feat.6c3b
```



```{r eval=FALSE, include=FALSE}
#
ggsave("figure1008/subset1.plot6.DAM.a1.pdf",
       width = 12.3, height = 2.5,
       plot = pp.feat.6a1)
ggsave("figure1008/subset1.plot6.DAM.a2.pdf",
       width = 12.3, height = 2.5,
       plot = pp.feat.6a2)

#
ggsave("figure1008/subset1.plot6.DAM.b1.pdf",
       width = 8, height = 6,
       plot = pp.feat.6b2)

#
ggsave("figure1008/subset1.plot6.DAM.c1.pdf",
       width = 12, height = 6,
       plot = pp.feat.6c2)

ggsave("figure1008/subset1.plot6.DAM.c2a.pdf",
       width = 12.5, height = 6,
       plot = pp.feat.6c3a)

ggsave("figure1008/subset1.plot6.DAM.c2b.pdf",
       width = 9.6, height = 8,
       plot = pp.feat.6c3b)

```



### plot7              

count DEG number, using different cutoffs         


```{r message=FALSE, warning=FALSE, paged.print=FALSE}
cut.padj = 0.05
cut.log2FC = 0.1   
  
cut.pct1 = 0.05

stat.a1 <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  summarise(up.DEGs = n()) %>% as.data.frame()
stat.a1
```

```{r message=FALSE, warning=FALSE}
pp.stat.DEG[["a1"]] <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  summarise(up.DEGs = n()) %>% as.data.frame() %>%
  ggplot(aes(x=contrast, y=up.DEGs, color = cluster)) +
  geom_bar(stat="summary", fun="mean", position = position_dodge(0.75), width = 0.58, fill="white") +
  geom_text(aes(label = up.DEGs),vjust=-0.21, show.legend = F, position = position_dodge(0.75) ) +
  theme_classic(base_size = 15) +
  scale_color_manual(values = color.cnt, name="") +
  labs(title=paste0("up.DEGs stat, pct.1>0.05, padj<",cut.padj,", |log2FC|>",cut.log2FC), y = "Number of DEGs") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6),
        title =element_text(size=12, face='bold'))
pp.stat.DEG[["a1"]]
```

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
cut.padj = 0.05
cut.log2FC = 0.2   
  
cut.pct1 = 0.05

stat.a2 <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  summarise(up.DEGs = n()) %>% as.data.frame()
stat.a2
```

```{r message=FALSE, warning=FALSE}
pp.stat.DEG[["a2"]] <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  summarise(up.DEGs = n()) %>% as.data.frame() %>%
  ggplot(aes(x=contrast, y=up.DEGs, color = cluster)) +
  geom_bar(stat="summary", fun="mean", position = position_dodge(0.75), width = 0.58, fill="white") +
  geom_text(aes(label = up.DEGs),vjust=-0.21, show.legend = F, position = position_dodge(0.75) ) +
  theme_classic(base_size = 15) +
  scale_color_manual(values = color.cnt, name="") +
  labs(title=paste0("up.DEGs stat, pct.1>0.05, padj<",cut.padj,", |log2FC|>",cut.log2FC), y = "Number of DEGs") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6),
        title =element_text(size=12, face='bold'))
pp.stat.DEG[["a2"]]
```

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
cut.padj = 0.05
cut.log2FC = 0.3   
  
cut.pct1 = 0.05

stat.a3 <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  summarise(up.DEGs = n()) %>% as.data.frame()
stat.a3
```

```{r message=FALSE, warning=FALSE}
pp.stat.DEG[["a3"]] <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  summarise(up.DEGs = n()) %>% as.data.frame() %>%
  ggplot(aes(x=contrast, y=up.DEGs, color = cluster)) +
  geom_bar(stat="summary", fun="mean", position = position_dodge(0.75), width = 0.58, fill="white") +
  geom_text(aes(label = up.DEGs),vjust=-0.21, show.legend = F, position = position_dodge(0.75) ) +
  theme_classic(base_size = 15) +
  scale_color_manual(values = color.cnt, name="") +
  labs(title=paste0("up.DEGs stat, pct.1>0.05, padj<",cut.padj,", |log2FC|>",cut.log2FC), y = "Number of DEGs") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 9.6),
        title =element_text(size=12, face='bold'))
pp.stat.DEG[["a3"]]
```



```{r eval=FALSE, include=FALSE}
#
ggsave("figure1008/subset1.plot7.DEG_stat.a1.pdf",
       width = 6, height = 4.8,
       plot = pp.stat.DEG[["a1"]])
write.csv(stat.a1, "figure1008/subset1.plot7.DEG_stat.a1.csv")

ggsave("figure1008/subset1.plot7.DEG_stat.a2.pdf",
       width = 6, height = 4.8,
       plot = pp.stat.DEG[["a2"]])
write.csv(stat.a2, "figure1008/subset1.plot7.DEG_stat.a2.csv")

ggsave("figure1008/subset1.plot7.DEG_stat.a3.pdf",
       width = 6, height = 4.8,
       plot = pp.stat.DEG[["a3"]])
write.csv(stat.a3, "figure1008/subset1.plot7.DEG_stat.a3.csv")
```



#### DEG list           

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
cut.padj = 0.05
cut.log2FC = 0.1   
  
cut.pct1 = 0.05

stat.a1.df <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  #summarise(up.DEGs = n()) %>% 
  as.data.frame()
dim(stat.a1.df)
stat.a1.df[1:6,]
```

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
cut.padj = 0.05
cut.log2FC = 0.2   
  
cut.pct1 = 0.05

stat.a2.df <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  #summarise(up.DEGs = n()) %>% 
  as.data.frame()
dim(stat.a2.df)
stat.a2.df[1:6,]
```


```{r message=FALSE, warning=FALSE, paged.print=FALSE}
cut.padj = 0.05
cut.log2FC = 0.3   
  
cut.pct1 = 0.05

stat.a3.df <- df.DEGs.a %>% filter(p_val_adj < cut.padj & 
                       abs(avg_log2FC) > cut.log2FC & 
                       pct.1 > cut.pct1) %>%
  group_by(contrast,cluster) %>%
  #summarise(up.DEGs = n()) %>% 
  as.data.frame()
dim(stat.a3.df)
stat.a3.df[1:6,]
```

```{r}
#
stat.a1.list <- list(P06.TDTvsCTR.CTRup = (stat.a1.df %>% filter(contrast == "P06.TDTvsCTR" & cluster == "P06.CTR"))$gene,
                     P06.TDTvsCTR.TDTup = (stat.a1.df %>% filter(contrast == "P06.TDTvsCTR" & cluster == "P06.TDT"))$gene,
                     P06.TDTvsMIG.MIGup = (stat.a1.df %>% filter(contrast == "P06.TDTvsMIG" & cluster == "P06.MIG"))$gene,
                     P06.TDTvsMIG.TDTup = (stat.a1.df %>% filter(contrast == "P06.TDTvsMIG" & cluster == "P06.TDT"))$gene,
                     P30.PBS.TDTvsCTR.CTRup = (stat.a1.df %>% filter(contrast == "P30.PBS.TDTvsCTR" & cluster == "P30.PBS.CTR"))$gene,
                     P30.PBS.TDTvsCTR.TDTup = (stat.a1.df %>% filter(contrast == "P30.PBS.TDTvsCTR" & cluster == "P30.PBS.TDT"))$gene,
                     P30.PBS.TDTvsMIG.MIGup = (stat.a1.df %>% filter(contrast == "P30.PBS.TDTvsMIG" & cluster == "P30.PBS.MIG"))$gene,
                     P30.PBS.TDTvsMIG.TDTup = (stat.a1.df %>% filter(contrast == "P30.PBS.TDTvsMIG" & cluster == "P30.PBS.TDT"))$gene)
stat.a2.list <- list(P06.TDTvsCTR.CTRup = (stat.a2.df %>% filter(contrast == "P06.TDTvsCTR" & cluster == "P06.CTR"))$gene,
                     P06.TDTvsCTR.TDTup = (stat.a2.df %>% filter(contrast == "P06.TDTvsCTR" & cluster == "P06.TDT"))$gene,
                     P06.TDTvsMIG.MIGup = (stat.a2.df %>% filter(contrast == "P06.TDTvsMIG" & cluster == "P06.MIG"))$gene,
                     P06.TDTvsMIG.TDTup = (stat.a2.df %>% filter(contrast == "P06.TDTvsMIG" & cluster == "P06.TDT"))$gene,
                     P30.PBS.TDTvsCTR.CTRup = (stat.a2.df %>% filter(contrast == "P30.PBS.TDTvsCTR" & cluster == "P30.PBS.CTR"))$gene,
                     P30.PBS.TDTvsCTR.TDTup = (stat.a2.df %>% filter(contrast == "P30.PBS.TDTvsCTR" & cluster == "P30.PBS.TDT"))$gene,
                     P30.PBS.TDTvsMIG.MIGup = (stat.a2.df %>% filter(contrast == "P30.PBS.TDTvsMIG" & cluster == "P30.PBS.MIG"))$gene,
                     P30.PBS.TDTvsMIG.TDTup = (stat.a2.df %>% filter(contrast == "P30.PBS.TDTvsMIG" & cluster == "P30.PBS.TDT"))$gene)
stat.a3.list <- list(P06.TDTvsCTR.CTRup = (stat.a3.df %>% filter(contrast == "P06.TDTvsCTR" & cluster == "P06.CTR"))$gene,
                     P06.TDTvsCTR.TDTup = (stat.a3.df %>% filter(contrast == "P06.TDTvsCTR" & cluster == "P06.TDT"))$gene,
                     P06.TDTvsMIG.MIGup = (stat.a3.df %>% filter(contrast == "P06.TDTvsMIG" & cluster == "P06.MIG"))$gene,
                     P06.TDTvsMIG.TDTup = (stat.a3.df %>% filter(contrast == "P06.TDTvsMIG" & cluster == "P06.TDT"))$gene,
                     P30.PBS.TDTvsCTR.CTRup = (stat.a3.df %>% filter(contrast == "P30.PBS.TDTvsCTR" & cluster == "P30.PBS.CTR"))$gene,
                     P30.PBS.TDTvsCTR.TDTup = (stat.a3.df %>% filter(contrast == "P30.PBS.TDTvsCTR" & cluster == "P30.PBS.TDT"))$gene,
                     P30.PBS.TDTvsMIG.MIGup = (stat.a3.df %>% filter(contrast == "P30.PBS.TDTvsMIG" & cluster == "P30.PBS.MIG"))$gene,
                     P30.PBS.TDTvsMIG.TDTup = (stat.a3.df %>% filter(contrast == "P30.PBS.TDTvsMIG" & cluster == "P30.PBS.TDT"))$gene)
```


```{r}
lapply(stat.a1.list,length)
```

```{r}
lapply(stat.a2.list,length)
```

```{r}
lapply(stat.a3.list,length)
```



```{r eval=FALSE, include=FALSE}
#
for(nn in names(stat.a1.list)){
  write.table(stat.a1.list[[nn]],paste0("figure1008/subset1.plot7.DEGlist/a1.log2FC_0.1.",nn,".txt"),row.names = F, col.names = F, quote = F)
}

#
for(nn in names(stat.a2.list)){
  write.table(stat.a2.list[[nn]],paste0("figure1008/subset1.plot7.DEGlist/a2.log2FC_0.2.",nn,".txt"),row.names = F, col.names = F, quote = F)
}

#
for(nn in names(stat.a3.list)){
  write.table(stat.a3.list[[nn]],paste0("figure1008/subset1.plot7.DEGlist/a3.log2FC_0.3.",nn,".txt"),row.names = F, col.names = F, quote = F)
}

```




### plot8              

DEG volcano, set same x/y-axis              


```{r fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
pp.DEGs.a$P06.TDTvsCTR <- DEGs.a.combine$P06.TDTvsCTR %>%
  mutate(label=ifelse(((p_val_adj < 1e-8 & avg_log2FC<0) | (p_val_adj < 1e-8 & avg_log2FC>0) | (p_val_adj < 0.05 & abs(avg_log2FC) > 0.5)) &
                        !grepl("^Gm|^Hsp|^Rps|^Rpl|Rik$|Xist|Tsix|Uty|Ddx3y|Eif2s3y|Kdm5d",gene),gene,""),
         sig.=ifelse(p_val_adj<0.05 & avg_log2FC<0,"CTR",ifelse(p_val_adj<0.05 & avg_log2FC>0,"TDT","None")),
         padj=ifelse(p_val_adj<1e-60,p_val_adj+1e-60,p_val_adj)) %>%
  ggplot(aes(y= -log10(padj), x=avg_log2FC, size=pct.1, label=label,fill=sig.)) +
  geom_point(shape=21, alpha=0.65) +
  geom_text_repel(size=2.5, max.overlaps = 500) +
  scale_fill_manual(values = c("CTR"="Skyblue",
                               "TDT"="pink",
                               "None"="grey")) +
  theme_classic() + labs(title="P06, TDT vs CTR") +
  guides(size = guide_legend(order = 2), fill=guide_legend(order = 1, reverse = F)) +
  geom_vline(xintercept = c(-0.1,0.1), linetype="dotted") + xlim(c(-1,1.75)) + ylim(c(0,60))
pp.DEGs.a$P06.TDTvsCTR
```


```{r fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
pp.DEGs.a$P06.TDTvsMIG <- DEGs.a.combine$P06.TDTvsMIG %>%
  mutate(label=ifelse(((p_val_adj < 1e-5 & avg_log2FC<0) | (p_val_adj < 1e-5 & avg_log2FC>0) | (p_val_adj < 0.05 & abs(avg_log2FC) > 0.5)) &
                        !grepl("^Gm|^Hsp|^Rps|^Rpl|Rik$|Xist|Tsix|Uty|Ddx3y|Eif2s3y|Kdm5d",gene),gene,""),
         sig.=ifelse(p_val_adj<0.05 & avg_log2FC<0,"MIG",ifelse(p_val_adj<0.05 & avg_log2FC>0,"TDT","None")),
         padj=ifelse(p_val_adj<1e-60,p_val_adj+1e-60,p_val_adj)) %>%
  ggplot(aes(y= -log10(padj), x=avg_log2FC, size=pct.1, label=label,fill=sig.)) +
  geom_point(shape=21, alpha=0.65) +
  geom_text_repel(size=2.5, max.overlaps = 500) +
  scale_fill_manual(values = c("MIG"="Skyblue",
                               "TDT"="pink",
                               "None"="grey")) +
  theme_classic() + labs(title="P06, TDT vs MIG") +
  guides(size = guide_legend(order = 2), fill=guide_legend(order = 1, reverse = F)) +
  geom_vline(xintercept = c(-0.1,0.1), linetype="dotted") + xlim(c(-1,1.75)) + ylim(c(0,60))
pp.DEGs.a$P06.TDTvsMIG
```


```{r fig.width=12, fig.height=6}
pp.DEGs.a$P30.PBS.TDTvsCTR <- DEGs.a.combine$P30.PBS.TDTvsCTR %>%
  mutate(label=ifelse(((p_val_adj < 1e-3 & avg_log2FC<0) | (p_val_adj < 1e-3 & avg_log2FC>0) | (p_val_adj < 0.05 & abs(avg_log2FC) > 0.5)) &
                        !grepl("^Gm|^Hsp|^Rps|^Rpl|Rik$|Xist|Tsix|Uty|Ddx3y|Eif2s3y|Kdm5d",gene),gene,""),
         sig.=ifelse(p_val_adj<0.05 & avg_log2FC<0,"CTR",ifelse(p_val_adj<0.05 & avg_log2FC>0,"TDT","None")),
         padj=ifelse(p_val_adj<1e-60,p_val_adj+1e-60,p_val_adj)) %>%
  ggplot(aes(y= -log10(padj), x=avg_log2FC, size=pct.1, label=label,fill=sig.)) +
  geom_point(shape=21, alpha=0.65) +
  geom_text_repel(size=2.5, max.overlaps = 500) +
  scale_fill_manual(values = c("CTR"="Skyblue",
                               "TDT"="pink",
                               "None"="grey")) +
  theme_classic() + labs(title="P30.PBS, TDT vs CTR") +
  guides(size = guide_legend(order = 2), fill=guide_legend(order = 1, reverse = F)) +
  geom_vline(xintercept = c(-0.1,0.1), linetype="dotted") + xlim(c(-1,1.75)) + ylim(c(0,60))
pp.DEGs.a$P30.PBS.TDTvsCTR
```


```{r fig.width=12, fig.height=6}
pp.DEGs.a$P30.PBS.TDTvsMIG <- DEGs.a.combine$P30.PBS.TDTvsMIG %>%
  mutate(label=ifelse(((p_val_adj < 1e-3 & avg_log2FC<0) | (p_val_adj < 1e-3 & avg_log2FC>0) | (p_val_adj < 0.05 & abs(avg_log2FC) > 0.5)) &
                        !grepl("^Gm|^Hsp|^Rps|^Rpl|Rik$|Xist|Tsix|Uty|Ddx3y|Eif2s3y|Kdm5d",gene),gene,""),
         sig.=ifelse(p_val_adj<0.05 & avg_log2FC<0,"MIG",ifelse(p_val_adj<0.05 & avg_log2FC>0,"TDT","None")),
         padj=ifelse(p_val_adj<1e-60,p_val_adj+1e-60,p_val_adj)) %>%
  ggplot(aes(y= -log10(padj), x=avg_log2FC, size=pct.1, label=label,fill=sig.)) +
  geom_point(shape=21, alpha=0.65) +
  geom_text_repel(size=2.5, max.overlaps = 500) +
  scale_fill_manual(values = c("MIG"="Skyblue",
                               "TDT"="pink",
                               "None"="grey")) +
  theme_classic() + labs(title="P30.PBS, TDT vs MIG") +
  guides(size = guide_legend(order = 2), fill=guide_legend(order = 1, reverse = F)) +
  geom_vline(xintercept = c(-0.1,0.1), linetype="dotted")  + xlim(c(-1,1.75)) + ylim(c(0,60))
pp.DEGs.a$P30.PBS.TDTvsMIG
```



```{r eval=FALSE, include=FALSE}
ggsave("figure1008/subset1.plot8.DEG_volcano.a1.pdf",
       width = 12, height = 6,
       plot = pp.DEGs.a$P06.TDTvsCTR)
ggsave("figure1008/subset1.plot8.DEG_volcano.a2.pdf",
       width = 12, height = 6,
       plot = pp.DEGs.a$P06.TDTvsMIG)
ggsave("figure1008/subset1.plot8.DEG_volcano.b1.pdf",
       width = 12, height = 6,
       plot = pp.DEGs.a$P30.PBS.TDTvsCTR)
ggsave("figure1008/subset1.plot8.DEG_volcano.b2.pdf",
       width = 12, height = 6,
       plot = pp.DEGs.a$P30.PBS.TDTvsMIG)
```


```{r}
#saveRDS(GEX.seur,"./Spp1tdt.subset1_P06_P30PBS.new1008.rds")
#GEX.seur <- readRDS("./Spp1tdt.subset1_P06_P30PBS.new1008.rds")
```



## newlist1009             


dotplot and violin in conditions           

```{r}
GEX.seur
```

```{r}
marker1009 <- as.vector(unlist(read.table("./dotplot.subset1_newlist1009.txt")))
marker1009
```


```{r}
length(marker1009)
sum(marker1009 %in% markers.new$gene)
```

```{r}
marker1009.sort <- (markers.new %>% group_by(cluster) %>% 
                  filter(gene %in% marker1009) %>%
                   ungroup() %>%
    #arrange(desc(avg_log2FC*pct.1),gene) %>%
    arrange(desc(avg_log2FC),gene) %>%
                             distinct(gene, .keep_all = TRUE) %>%
                             arrange(cluster,p_val_adj))$gene
```


```{r}
length(marker1009)
length(marker1009.sort)
setdiff(marker1009,marker1009.sort)
```

```{r}
marker1009.new <- c(marker1009.sort[1:15],"Fcrls",marker1009.sort[16:24])
```


```{r fig.width=7.5,fig.height=3.5}
pp.dot.x1a <- DotPlot(GEX.seur, features = marker1009, group.by = "new_clusters"
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters")
pp.dot.x1a
```

```{r fig.height=3.5, fig.width=7.5, message=FALSE}
pp.dot.x1a <- DotPlot(GEX.seur, features = marker1009.new, group.by = "new_clusters",cols = c("lightgrey","red")
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Clusters")
pp.dot.x1a

pp.dot.x1a  + scale_color_gradientn(colours  = rev(mapal))
```


```{r fig.height=3, fig.width=7.8, message=FALSE}
pp.dot.x1b <- DotPlot(GEX.seur, features = marker1009.new, group.by = "cnt",cols = c("lightgrey","red")
                         ) +
                 theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) + labs(y="Conditions")
pp.dot.x1b

pp.dot.x1b  + scale_color_gradientn(colours  = rev(mapal))

```



```{r fig.height=15.5, fig.width=18, message=FALSE, warning=FALSE}
pp.violin.x1b <- VlnPlot(GEX.seur, features = marker1009.new, group.by = "cnt", cols = color.cnt,
                      ncol = 5, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55)
pp.violin.x1b
```


```{r fig.height=18.5, fig.width=18, message=FALSE, warning=FALSE}
pp.violin.x1c <- VlnPlot(GEX.seur, features = marker1009.new, group.by = "cnt", cols = color.cnt,
                      ncol = 5, pt.size = 0, raster = F) & geom_boxplot(outlier.size = 0, fill="white", width=0.3, size=0.1, alpha=0.55) &
  stat_summary(fun=mean, geom="point", shape=18, size=2, color="black", alpha=0.55) & ylim(c(0,7.2)) &
  ggpubr::stat_compare_means(aes(lable = ..p.signif..), 
                               method = "wilcox.test",
                               comparisons = list(c("P06.CTR","P06.MIG"),
                                                  c("P06.MIG","P06.TDT"),
                                                  c("P06.CTR","P06.TDT"),
                                                  c("P30.PBS.CTR","P30.PBS.MIG"),
                                                  c("P30.PBS.MIG","P30.PBS.TDT"),
                                                  c("P30.PBS.CTR","P30.PBS.TDT"),
                                                  c("P06.TDT","P30.PBS.TDT")),
                               label.y = c(6.3,6.8,7.3,6.3,6.8,7.3,7.8)-1,
                               size=1.75
                               )
pp.violin.x1c
```



```{r eval=FALSE, include=FALSE}
ggsave("figure1008/subset1.newlist.dot.a1.pdf",
       width = 7.6,height = 3.5,
       plot = pp.dot.x1a )
ggsave("figure1008/subset1.newlist.dot.a2.pdf",
       width = 7.6,height = 3.5,
       plot = pp.dot.x1a  + scale_color_gradientn(colours  = rev(mapal)))

ggsave("figure1008/subset1.newlist.dot.b1.pdf",
       width = 8.4,height = 3,
       plot = pp.dot.x1b )
ggsave("figure1008/subset1.newlist.dot.b2.pdf",
       width = 8.4,height = 3,
       plot = pp.dot.x1b  + scale_color_gradientn(colours  = rev(mapal)))

write.table(marker1009.new, "figure1008/subset1.newlist.sort.txt", row.names = F, col.names = F, quote = F)

ggsave("figure1008/subset1.newlist.violin.b1.pdf",
       width = 18, height = 15.5,
       plot = pp.violin.x1b)

ggsave("figure1008/subset1.newlist.violin.b2.pdf",
       width = 18, height = 18.5,
       plot = pp.violin.x1c)
```



## forGEO            


```{r}
GEX.seur <- readRDS("./Spp1tdt.subset1_P06_P30PBS.new1008.rds")
GEX.seur
```


```{r paged.print=FALSE}
GEX.seur@meta.data[,grep("snn|pANN",colnames(GEX.seur@meta.data),value = T)] <- NULL
head(GEX.seur@meta.data)
```


```{r}
#saveRDS(GEX.seur,"I:/Shared_win/projects/202310_Spp1DAM/forGEO/seur_obj/Spp1TDT_P06P30.final.seur_obj.rds")
```






